---
title: "Mesocosm experiment: Traits analysis"
author: "Laure Olazcuaga"
date: "`r format(Sys.Date(), '%d-%B-%Y')`"
output: 
  html_document:
    theme: "journal"
    toc: true
    toc_depth: 3
    number_sections: true
    toc_float:
      collapsed: false
      smooth_scroll: false
editor_options: 
  chunk_output_type: console
---


```{r setup, include =FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
devtools::load_all()

```


    
# DATASET
## Open dataset
```{r }
# library(dplyr)
# library(lme4)
# library(MuMIn) #R2 explained
# library(r2glmm) #R2 explained
# library(splines)
# library(nlme)
# library(glmmTMB)
#####################
## 1 ## DECOMPOSITION 
#####################
data_decompo <-  read.csv(file=here::here("data",
                                          "../DATA/Decomposition.csv"))
head(data_decompo)


pd <- position_dodge(0.25) # move them .05 to the left and right


#####################
## 2 ## RESPIRO 
#####################
data_respiro <- read.csv(file=here::here("data",
                                         "../DATA/Data_respirometry_Asellus2025.csv"))
head(data_respiro)

#####################
## 3 ## SIZE 
#####################
data_length <- read.csv(file=here::here("data",
                                        "../DATA/Data_length_Asellus2025.csv"))
head(data_length)

#####################
## 4 ## Mass_Ind 
#####################
#MASS_IND_EXPECTED = (MASS_POP * SIZE_IND) / SIZE_POP = (MASS_POP / SIZE_POP) * SIZE_IND 
data_mass <- read.csv(file=here::here("data",
                                      "../DATA/Data_weight_Asellus2025.csv"))

``` 


## Add Ratio Mass
```{r }
  #MASS_IND_EXPECTED = (MASS_POP * SIZE_IND) / SIZE_POP = (MASS_POP / SIZE_POP) * SIZE_IND 
data_mass$Ratio <- data_mass$Mass / data_mass$Size


MEAN_RATIO <- mean(data_mass$Ratio)

### Option alternative : 
data_mass$log_mass <- log(data_mass$Mass)
data_mass$log_size <- log(data_mass$Size)
lm_masssize <- lm(log_mass ~ log_size, data = data_mass)

a_log <- coef(lm_masssize)[1]  # intercept (log(a))
b <- coef(lm_masssize)[2]      # slope (b)
a <- exp(a_log)

 




######## REMOVE ALL PART BELOW BECAUSE not enough values per pop or per evol history 
#to correctly estimate the ratio per pop or per evol history 
#This leads to a bias and biases the weight estimates 
#So a single ratio is estimated for all values.

# ### Extract mean for Pred_Warm (B7) and  Pred_Ambiant (B6)
## Function: one mean for all values matching pop_vec
# get_mean_ratio <- function(pop_vec) {
#   subset_data <- data_mass[data_mass$Bac %in% pop_vec, ]
#   mean(subset_data$Ratio)
# }
# 
# ## Apply for each vector
# mean_ratio_NoPredAmbiant <- get_mean_ratio(pop_NoPredAmbiant)
# mean_ratio_NoPredWarm    <- get_mean_ratio(pop_NoPredWarm)
# mean_ratio_PredAmbiant   <- get_mean_ratio(pop_PredAmbiant)
# mean_ratio_PredWarm      <- get_mean_ratio(pop_PredWarm)

## Results
# mean_ratio_NoPredAmbiant
# mean_ratio_NoPredWarm
# mean_ratio_PredAmbiant
# mean_ratio_PredWarm


## Function: one mean for all values matching pop_vec
# get_length_ratio <- function(pop_vec) {
#   subset_data <- data_mass[data_mass$Bac %in% pop_vec, ]
#   length(subset_data$Ratio)
# }

## Apply for each vector
#get_length_ratio(pop_PredAmbiant)
#get_length_ratio(pop_PredWarm)


# 
# #Run after all the dataset chuncks:
# datatest <- data_mass %>%
#   left_join(
#     datamerged %>%
#       distinct(Pop, .keep_all = TRUE) %>%  # garde la 1ère ligne par Pop
#       select(Pop, Tpop,Predpop),
#     by = c("Bac" = "Pop")
#   )
# datatest$EvolHistory <- paste0(datatest$Predpop,"_",datatest$Tpop)


# 
# data_mass_pop <- Rmisc::summarySE(data = data_mass,measurevar ="Ratio","Bac")
# data_mass_evolhistory <- Rmisc::summarySE(data = datatest,measurevar ="Ratio","EvolHistory")





# ggplot(data=datatest, aes(x=Mass, y = Size, color = Bac)) + 
#   facet_wrap(~ Bac) +
#   geom_point()

# ggplot(data=datatest, aes(x=Mass, y = Size, color = Bac)) + 
#   facet_wrap(~ EvolHistory) +
#   geom_point()
# 
# ggplot(datatest, aes(x = Ratio, y = Bac, color = EvolHistory)) +
#   geom_point(position = position_jitter(width = 0, height = 0)) +
#   theme_minimal()
# 
# ggplot(data=datatest, aes(x=Mass, y = Size, color = EvolHistory)) + 
#   facet_wrap(~ EvolHistory) +
#   geom_point()

# ggplot(datatest, aes(x = Mass, y = Bac, color = EvolHistory)) +
#   geom_point(position = position_jitter(width = 0.2, height = 0)) +
#   theme_minimal()
# ggplot(datatest, aes(x = Ratio, y = Bac, color = EvolHistory)) +
#   geom_point(position = position_jitter(width = 0.2, height = 0)) +
#   theme_minimal()
# # 



################## ADD RATIO TO ORIGINAL DATASET

##### OPTION 1
### ONE RATIO PER POP
# datamerged <- datamerged %>%
#   left_join(data_mass_pop %>% select(Bac, Ratio), 
#             by = c("Pop" = "Bac" ))
# head(datamerged)
# 
# ### Add Ratio for B6 and B7 
# datamerged$Ratio[datamerged$Pop=="B6"] <- mean_ratio_PredAmbiant
# datamerged$Ratio[datamerged$Pop=="B7"] <- mean_ratio_PredWarm

##### OPTION 2
###ONLY ONE RATIO PER EVOLHISTORY
# datamerged <- datamerged %>%
#   left_join(data_mass_evolhistory %>% select(EvolHistory, Ratio), 
#             by = c("EvolHistory" = "EvolHistory" ))
# head(datamerged)



### OPTION3 ONE RATIO 
data_length$Ratio <- MEAN_RATIO

# Add Individual mass
#data_length$Mass_Ind2 <- data_length$Ratio * data_length$Length
#data_length$Mass_Ind2 <- intercept_mass + slope_mass*data_length$Length

data_length$Mass_Ind <- a*(data_length$Length^b)

#plot(data_length$Mass_Ind ~ data_length$Mass_Ind2)


# As factor
data_length$Tpop <- as.factor(data_length$Tpop)
data_length$Pop <- as.factor(data_length$Pop)
data_length$Predpop <- as.factor(data_length$Predpop)


## CHECK OUTLIER
head(data_length[order(data_length$Mass_Ind), ], 5)
#Extreme and aberrant values : 
data_length <- data_length[data_length$Mass_Ind >= 0.02,]



``` 







## Merge Length and respiro 
```{r }
keys = c("Ref", "ID_photo", "Round", "TempExp", "Reader", "TempExpNum", "Pop", 
         "PopInd", "Tpop", "Predpop", "Survival", "Naivety")
keys = intersect(names(data_length), names(data_respiro))



# Merge
datamerged <- merge(
  data_length, data_respiro,
  by = keys,
  all = TRUE,
  suffixes = c(".len", ".resp"))

# --- Simple mismatch check ---
common_cols <- intersect(names(data_length), names(data_respiro))
common_cols <- setdiff(common_cols, keys)

for (col in common_cols) {
  col_len  <- paste0(col, ".len")
  col_resp <- paste0(col, ".resp")
  if (all(col_len %in% names(datamerged), col_resp %in% names(datamerged))) {
    mismatch <- sum(datamerged[[col_len]] != datamerged[[col_resp]], na.rm = TRUE)
    if (mismatch > 0) {
      warning(sprintf("Column %s has %d mismatched values", col, mismatch))
    }
  }
}

head(datamerged)

# --- 2. Clean merged dataset ---
# Remove rows that are completely NA
dim(datamerged)
datamerged <- datamerged[rowSums(is.na(datamerged)) < ncol(datamerged), ]

``` 



## Estimate DecompoRate
```{r }

head(data_decompo)

#REmove useless columns
data_decompo_clean <- data_decompo[,c(1:10)]

#Add usefull columns
data_decompo_clean$EvolHistory <- as.factor(paste0(data_decompo_clean$Predpop,
                                                   "_",
                                        data_decompo_clean$Tpop))

#Determine as factor 
data_decompo_clean$Tpop <- as.factor(data_decompo_clean$Tpop)
data_decompo_clean$Pop <- as.factor(data_decompo_clean$Pop)
data_decompo_clean$Predpop <- as.factor(data_decompo_clean$Predpop)


#check mortality similar across groups
tapply(data_decompo_clean$Mortality,data_decompo_clean$TempExpNum, 
       mean, na.rm=TRUE)
tapply(data_decompo_clean$Mortality,data_decompo_clean$EvolHistory, 
       mean, na.rm=TRUE)
#Mortality is similar across groups 
head(data_decompo_clean)


### Add degradration percent
data_decompo_clean$Deg_Rate <- data_decompo_clean$Deg_Weight/
  data_decompo_clean$InWeight
#Deg_Rate is the percent of mass lost 

# plot(data_decompo_clean$Deg_Rate ~ data_decompo_clean$Mortality)

## Consider control treatment: For the weigth 
SUM_deg_control <- Rmisc::summarySE(data_decompo_clean[data_decompo_clean$Pop=="C",],
                  measurevar = "Deg_Weight",
                  groupvars = c("TempExpNum"))
  
data_decompo_clean <- merge(data_decompo_clean, 
                     SUM_deg_control[, c("TempExpNum", "Deg_Weight")], 
                     by = "TempExpNum", 
                     all.x = TRUE)

colnames(data_decompo_clean)[colnames(data_decompo_clean) == "Deg_Weight.x"] <- "Deg_Weight"
colnames(data_decompo_clean)[colnames(data_decompo_clean) == "Deg_Weight.y"] <- "Deg_Weight_Control"


head(data_decompo_clean)


# Pour info:
SUM_deg <- Rmisc::summarySE(data_decompo_clean[data_decompo_clean$Pop!="C",],
                  measurevar = "Deg_Rate",
                  groupvars = c("TempExpNum"))


## Consider control treatment: For the rate 
SUM_deg_control <- Rmisc::summarySE(data_decompo_clean[data_decompo_clean$Pop=="C",],
                  measurevar = "Deg_Rate",
                  groupvars = c("TempExpNum"))
data_decompo_clean <- merge(data_decompo_clean, 
                     SUM_deg_control[, c("TempExpNum", "Deg_Rate")], 
                     by = "TempExpNum", 
                     all.x = TRUE)
colnames(data_decompo_clean)[colnames(data_decompo_clean) == "Deg_Rate.x"] <- "Deg_Rate"
colnames(data_decompo_clean)[colnames(data_decompo_clean) == "Deg_Rate.y"] <- "Deg_Rate_Control"

head(data_decompo_clean) 

#Calculate Degradation rate normalized : Deg_Rate -  Deg_Rate_Control
data_decompo_clean$Deg_Rate_Norm <- data_decompo_clean$Deg_Rate - data_decompo_clean$Deg_Rate_Control

#Remove controle of the dataset
data_decompo_clean_withcontrol <- data_decompo_clean
data_decompo_clean <- data_decompo_clean[data_decompo_clean$EvolHistory!="C_C",]


# check distribution : Rate ? 
hist(data_decompo_clean$Deg_Rate_Norm)
max(data_decompo_clean$Deg_Rate_Norm)
min(data_decompo_clean$Deg_Rate_Norm)
hist(data_decompo_clean$Deg_Rate_Norm)






#The decomposition rate was estimated over 17 days as k = −ln(X)/t [Zhang et al. 2018 and Raffard et al. 2008, Raffard et al. 2021], where X is the proportion of litter remaining after consumption by the group of 10 individuals and t the time elapsed in days. 

#-(log(10/100)/17) # Rate = 0.13 il en reste peu donc le rate est fort
#-(log(90/100)/17) # Rate = 0.0006 il en reste beaucoup donc le rate est faible

head(data_decompo_clean)

data_decompo_clean$Deg_Rate_Raffard <- -(log( data_decompo_clean$OutWeight/
  data_decompo_clean$InWeight)/17)

tapply(data_decompo_clean$Deg_Rate_Raffard, data_decompo_clean$Pop, length)
tapply(data_decompo_clean$Deg_Rate_Raffard, list(data_decompo_clean$Pop,data_decompo_clean$TempExpNum) , length)

``` 

## Correct datamerge
```{r }
#Estimate Slope corrected by the weight 
datamerged$Slope_Corrected <- datamerged$Slope/datamerged$Mass_Ind

#datamerged <- datamerged[!is.na(datamerged$Slope_Corrected),]
datamerged$TempExpNumSquare <- datamerged$TempExpNum*datamerged$TempExpNum


datamerged$EvolHistory <- as.factor(paste0(datamerged$Predpop,
                                                   "_",
                                        datamerged$Tpop))


#Remove NA lines
datamerged <- datamerged[!is.na(datamerged$Round),]


#Remove the extreme outlier after visual check of the photo of this invidiual
min(datamerged$Length, na.rm = TRUE)
datamerged[datamerged$Length==0.032,]
datamerged <- datamerged[datamerged$Ref!="T25_B4_Az5_B3",]



#Data Respiro 
datamerged_respiro <- datamerged[datamerged$r2 >= 0.85, ]
dim(datamerged_respiro)
datamerged_respiro <- datamerged_respiro[datamerged_respiro$Slope <= 0, ]
dim(datamerged_respiro)
datamerged_respiro <- datamerged_respiro[!is.na(datamerged_respiro$Slope),]


#Transform concentration of oxygen -> consomation of oxygen
datamerged_respiro$Slope_Pos <- -datamerged_respiro$Slope



##### HERE ISSUE 
cols_needed <- c("Slope_Pos", "TempExpNum", "Mass_Ind", "Pop")
datamerged_respiro_clean <- datamerged_respiro[complete.cases(datamerged_respiro[, cols_needed]), ]




#NUMBER OF REPLICATES PER POP 
#Mean per treatment
mean(tapply(datamerged$Mass_Ind,list(datamerged$TempExpNum, datamerged$Pop), length))

#Mean of the total number of individuals per pop
mean(tapply(datamerged$Mass_Ind,datamerged$Pop, sum, na.rm=TRUE))

#Mean of the total number of individuals per pop
mean(tapply(data_decompo_clean$InWeight,data_decompo_clean$Pop, sum, na.rm=TRUE), na.rm=TRUE)
mean(tapply(data_decompo_clean$InWeight,data_decompo_clean$Pop, sum, na.rm=TRUE), na.rm=TRUE)

mean(tapply(data_decompo_clean$InWeight,
            list(data_decompo_clean$TempExpNum, data_decompo_clean$Pop), length))
#Par pop : 9 groupes 

``` 



# FIGURE
## Figure Mass_Ind
```{r }

head(datamerged)
ggplot(data = datamerged) + 
  geom_boxplot(aes(y = Mass_Ind, x = TempExp, 
                   group = interaction(TempExp,Tpop,Predpop), 
                   col = interaction(Tpop,Predpop))) +
  theme_LO_sobre




ggplot(data = datamerged) + 
  geom_boxplot(aes(y = Mass_Ind, x = interaction(Tpop,Predpop), 
                   group = interaction(Tpop,Predpop), 
                   col = interaction(Tpop,Predpop))) +
  guides(colour = "none", 
         fill = "none") + 
    xlab("Experimental history") + 
  theme_LO_sobre


ggplot(data = datamerged) + 
  geom_jitter(aes(y = Mass_Ind, x = interaction(Tpop,Predpop), 
                   group = interaction(Tpop,Predpop), 
                   col = interaction(Tpop,Predpop))) +
  guides(colour = "none", 
         fill = "none") + 
    xlab("Experimental history") + 
  theme_LO_sobre


# ggplot(data = datamerged) + 
#   add_phylopic(x = 2, y = 1, img = img, alpha = 1, ysize = 0.05) + 
#   theme_LO_sobre



library(rphylopic)
uuid <- get_uuid(name = "Phoxinus phoxinus", n = 1)
img <- get_phylopic(uuid = uuid)
#View(datamerged)

plot_mass <- ggplot(data = datamerged) + 
  facet_wrap(~ Tpop, labeller = labeller(Tpop = 
                                           c("Ambiant" = "Ambient",
                                        "Warm" = "Warm"))) +
  add_phylopic(x = 2, y = 4.8, img = img, alpha = 1, ysize = 0.3) +
  geom_boxplot(aes(y = Mass_Ind, x = Predpop, 
                   group = interaction(Tpop,Predpop), 
                   col = interaction(Tpop,Predpop)), outliers = FALSE) +
    geom_jitter(aes(y = Mass_Ind, x = Predpop, 
                   group = interaction(Tpop,Predpop), 
                   col = interaction(Tpop,Predpop),
                   shape = interaction(Tpop,Predpop)), 
                size = 0.8, alpha = 0.4, width = 0.35) +
  scale_x_discrete(labels = c("Ctrl" = "Control", 
                              "Pred" = "Predator", 
                              "Ctrl" = "Control", 
                              "Pred" = "Predator")) +
  guides(colour = "none", 
         fill = "none",
         shape = "none") + 
    xlab("Evolutionary conditions") + 
    ylab("Body mass") + 
  scale_shape_manual(values = c(16,16,17,17)) +  
  scale_color_manual(values = c("#92c5de","#f4a582","#0571b0","#ca0020")) +
  theme_LO_sobre + 
  theme(strip.background = element_rect(fill = "white", 
                                        colour = "grey10", size = 0.4),
        strip.text = element_text(size = 10, face = "bold", colour = "black"))
plot_mass



plot_size <- ggplot(data = datamerged) + 
  facet_wrap(~ Tpop, labeller = labeller(Tpop = 
                                           c("Ambiant" = "Ambient",
                                        "Warm" = "Warm"))) +
  add_phylopic(x = 2, y = 0.2, img = img, alpha = 1, 
               ysize = 0.009) +
  geom_boxplot(aes(y = Length, x = Predpop, 
                   group = interaction(Tpop,Predpop), 
                   col = interaction(Tpop,Predpop)), outliers = FALSE) +
    geom_jitter(aes(y = Length, x = Predpop, 
                   group = interaction(Tpop,Predpop), 
                   col = interaction(Tpop,Predpop),
                   shape = interaction(Tpop,Predpop)), 
                size = 0.8, alpha = 0.4, width = 0.35) +
  scale_x_discrete(labels = c("Ctrl" = "Control", 
                              "Pred" = "Predator", 
                              "Ctrl" = "Control", 
                              "Pred" = "Predator")) +
  guides(colour = "none", 
         fill = "none",
         shape = "none") + 
    xlab("Evolutionary conditions") + 
    ylab("Body size") + 
  scale_shape_manual(values = c(16,16,17,17)) +  
  scale_color_manual(values = c("#92c5de","#f4a582","#0571b0","#ca0020")) +
  theme_LO_sobre + 
  theme(strip.background = element_rect(fill = "white", 
                                        colour = "grey10", size = 0.4),
        strip.text = element_text(size = 10, face = "bold", colour = "black"))
plot_size
# cowplot::save_plot("Plot_Mass_withratioEvolHistory.pdf",
#                    plot_mass, base_height = 9/cm(1),
#                    base_width = 12/cm(1), dpi = 610)
# 



PLOT_ALL2 <- cowplot::ggdraw() + 
  cowplot::draw_plot(plot_mass + guides(col="none", fill="none", shape="none"), 
            x = 0.01, y = 0, width = 0.5, height = 0.98) + 
  cowplot::draw_plot(plot_size , 
            x = 0.5, y = 0, width = 0.5, height = 0.98) + 
  cowplot::draw_plot_label(c("A", 
                             "B"),   
                  x = c(0.03,0.53), 
                  y = c(1, 1), 
                  hjust = c(-0.25, -0.25), 
                  vjust = c(1.5, 1.5),
                  size = 16) 
 PLOT_ALL2

 #head(datamerged[order(datamerged$Length), ], 5)

 
# cowplot::save_plot("Plot_Fig3_Length_Mass.pdf",
#                    PLOT_ALL2, base_height = 9/cm(1),
#                    base_width = 20/cm(1), dpi = 610)

``` 







## Figure Respiro
```{r }

ggplot(data = datamerged) + 
  geom_boxplot(aes(y = Slope, x = TempExp, 
                   group = interaction(TempExp,Tpop,Predpop), 
                   col = interaction(Tpop,Predpop))) +
  theme_LO_sobre

plot_rawdata <- ggplot(data = datamerged) + 
  geom_boxplot(aes(y = Slope_Corrected, x = TempExp, 
                   group = interaction(TempExp,Tpop,Predpop), 
                   col = interaction(Tpop,Predpop)), outlier.colour = "white") +
  geom_jitter(aes(y = Slope_Corrected, x = TempExp, 
                   group = interaction(TempExp,Tpop,Predpop), 
                   col = interaction(Tpop,Predpop)), alpha = 0.8 , size = 0.5) +
  theme_LO_sobre


# plot_rawdata <- ggplot(data = datamerged) + 
#   geom_histogram(aes(x = Slope_Corrected)) +
#   theme_LO_sobre


## OUTLIER EMMA 
# Calculer l'IQR du jeu de données
q1 <- quantile(datamerged$Slope_Corrected, 0.25)
q3 <- quantile(datamerged$Slope_Corrected, 0.75)
iqr <- q3 - q1
# Définir la plage de valeurs acceptables
lower <- q1 - 1.5 * iqr
upper <- q3 + 1.5 * iqr

plot_rawdata + 
  geom_hline(yintercept = lower) + 
  geom_hline(yintercept = upper) 


ggplot(data = datamerged) +
  geom_smooth(aes(y = Slope, x = TempExpNum,
                   col = interaction(Tpop,Predpop)), size = 0.5) +
  theme_LO_sobre



ggplot(data = datamerged) +
  geom_point(aes(y = Slope, x = Length,
                   col = interaction(Tpop,Predpop)), size = 0.5) +
  theme_LO_sobre



ggplot(data = datamerged) +
  geom_point(aes(y = Slope, x = Mass_Ind,
                   col = interaction(Tpop,Predpop)), size = 0.5) +
  theme_LO_sobre


plot_length <- ggplot(data = datamerged) +
  geom_point(aes(y = Slope, x = Length,
                   col = TempExp), size = 0.5) +
  theme_LO_sobre
plot_length

plot_mass <- ggplot(data = datamerged) +
  geom_point(aes(y = Slope, x = Mass_Ind,
                   col = TempExp), size = 0.5) +
  theme_LO_sobre
plot_mass





plot_length2 <- ggplot(data = datamerged) +
  geom_point(aes(y = Slope, x = Length,
                           color = interaction(Predpop,Tpop), 
                           shape = interaction(Predpop,Tpop)), 
             size = 1, alpha = 0.8) +
    scale_shape_manual(name = "Evolution history",
                    labels=c("Ctrl.Ambiant" = "Ambient x NoPred" ,
                             "Pred.Ambiant" = "Ambient x Pred" ,
                              "Ctrl.Warm" = "Warm x NoPred",
                             "Pred.Warm" = "Warm x Pred" ),
                    values = c(16,17,16,17)) +  
  scale_color_manual(name = "Evolution history",
                    labels=c("Ctrl.Ambiant" = "Ambient x NoPred" ,
                             "Pred.Ambiant" = "Ambient x Pred" ,
                              "Ctrl.Warm" = "Warm x NoPred",
                             "Pred.Warm" = "Warm x Pred" ),
                    values = c("#92c5de","#0571b0","#f4a582","#ca0020")) +
  theme_LO_sobre
plot_length2

plot_mass2 <- ggplot(data = datamerged) +
  geom_point(aes(y = Slope, x = Mass_Ind,
                           color = interaction(Predpop,Tpop), 
                           shape = interaction(Predpop,Tpop)), 
             size = 1, alpha = 0.8) +
    scale_shape_manual(name = "Evolution history",
                    labels=c("Ctrl.Ambiant" = "Ambient x NoPred" ,
                             "Pred.Ambiant" = "Ambient x Pred" ,
                              "Ctrl.Warm" = "Warm x NoPred",
                             "Pred.Warm" = "Warm x Pred" ),
                    values = c(16,17,16,17)) +  
  scale_color_manual(name = "Evolution history",
                    labels=c("Ctrl.Ambiant" = "Ambient x NoPred" ,
                             "Pred.Ambiant" = "Ambient x Pred" ,
                              "Ctrl.Warm" = "Warm x NoPred",
                             "Pred.Warm" = "Warm x Pred" ),
                    values = c("#92c5de","#0571b0","#f4a582","#ca0020")) +
  theme_LO_sobre
plot_mass2













PLOT_ALL <- cowplot::ggdraw() + 
  cowplot::draw_plot(plot_length + guides(col="none"), 
            x = 0.01, y = 0, width = 0.4, height = 0.98) + 
  cowplot::draw_plot(plot_mass , 
            x = 0.43, y = 0, width = 0.58, height = 0.98) + 
  cowplot::draw_plot_label(c("A", 
                             "B"),   
                  x = c(0.01,0.43), 
                  y = c(1, 1), 
                  hjust = c(-0.25, -0.25), 
                  vjust = c(1.5, 1.5),
                  size = 16) 
 PLOT_ALL

 
 
PLOT_ALL2 <- cowplot::ggdraw() + 
  cowplot::draw_plot(plot_length2 + guides(col="none", fill="none", shape="none"), 
            x = 0.01, y = 0, width = 0.4, height = 0.98) + 
  cowplot::draw_plot(plot_mass2 , 
            x = 0.4, y = 0, width = 0.6, height = 0.98) + 
  cowplot::draw_plot_label(c("A", 
                             "B"),   
                  x = c(0.01,0.43), 
                  y = c(1, 1), 
                  hjust = c(-0.25, -0.25), 
                  vjust = c(1.5, 1.5),
                  size = 16) 
 PLOT_ALL2

 
# cowplot::save_plot("Plot_Correlation_Respiro_vs_SizeMass_ColTemp.pdf",
#                    PLOT_ALL, base_height = 9/cm(1),
#                    base_width = 20/cm(1), dpi = 610)
# cowplot::save_plot("Plot_Correlation_Respiro_vs_SizeMass_ColExp.pdf",
#                    PLOT_ALL2, base_height = 9/cm(1),
#                    base_width = 20/cm(1), dpi = 610)
#  
 
 
 
 
 
 ### IMPORTANT ONE
 
 
plot_mass2 <- ggplot(data = datamerged_respiro_clean) +
  facet_wrap( ~ TempExp, nrow = 2) +
  geom_point(aes(y = log(Slope_Pos), x = log(Mass_Ind),
                           color = interaction(Predpop,Tpop), 
                           shape = interaction(Predpop,Tpop)), 
             size = 1, alpha = 0.8) +
    scale_shape_manual(name = "Evolution history",
                    labels=c("Ctrl.Ambiant" = "Ambient x NoPred" ,
                             "Pred.Ambiant" = "Ambient x Pred" ,
                              "Ctrl.Warm" = "Warm x NoPred",
                             "Pred.Warm" = "Warm x Pred" ),
                    values = c(16,17,16,17)) +  
  scale_color_manual(name = "Evolution history",
                    labels=c("Ctrl.Ambiant" = "Ambient x NoPred" ,
                             "Pred.Ambiant" = "Ambient x Pred" ,
                              "Ctrl.Warm" = "Warm x NoPred",
                             "Pred.Warm" = "Warm x Pred" ),
                    values = c("#92c5de","#0571b0","#f4a582","#ca0020")) +
  theme_LO_sobre
plot_mass2


cowplot::save_plot("Plot_LogSlope_LogMass_Temp.pdf",
                   plot_mass2, base_height = 12/cm(1),
                   base_width = 20/cm(1), dpi = 610)
#  

``` 



## Figure Decompo
```{r }
PLOT_DECOMPO <- ggplot(data = data_decompo_clean_withcontrol) + 
  geom_boxplot(aes(y = Deg_Rate, x = TempExp, 
                   col = EvolHistory)) +
  scale_color_manual(name = "Evolution history",
                    labels=c("C_C"="Control",
                             "Ctrl_Ambiant" = "Ambient x NoPred" ,
                             "Pred_Ambiant" = "Ambient x Pred" ,
                              "Ctrl_Warm" = "Warm x NoPred",
                             "Pred_Warm" = "Warm x Pred" ),
                    values = c("Black","#92c5de","#f4a582","#0571b0","#ca0020")) +
  ylab("Decomposition rate") + 
  xlab("Experimental temperature") + 
  ylim(0.05,0.5) + 
  theme_LO_sobre
PLOT_DECOMPO


PLOT_DECOMPO2 <- ggplot(data = data_decompo_clean) + 
  geom_boxplot(aes(y = Deg_Rate_Norm, x = TempExp, 
                   col = EvolHistory)) +
  scale_color_manual(name = "Evolution history",
                    labels=c("Ctrl_Ambiant" = "Ambient x NoPred" ,
                             "Pred_Ambiant" = "Ambient x Pred" ,
                              "Ctrl_Warm" = "Warm x NoPred",
                             "Pred_Warm" = "Warm x Pred" ),
                    values = c("#92c5de","#f4a582","#0571b0","#ca0020")) +
  ylab("Decomposition rate - Control Rate") + 
  xlab("Experimental temperature") + 
    ylim(0.05,0.5) + 
theme_LO_sobre
PLOT_DECOMPO2


PLOT_ALL2 <- cowplot::ggdraw() + 
  cowplot::draw_plot(PLOT_DECOMPO + guides(col="none", fill="none", shape="none"), 
            x = 0.01, y = 0, width = 0.4, height = 0.98) + 
  cowplot::draw_plot(PLOT_DECOMPO2 , 
            x = 0.4, y = 0, width = 0.6, height = 0.98) + 
  cowplot::draw_plot_label(c("A", 
                             "B"),   
                  x = c(0.01,0.4), 
                  y = c(1, 1), 
                  hjust = c(-0.25, -0.25), 
                  vjust = c(1.5, 1.5),
                  size = 16) 
 PLOT_ALL2

# cowplot::save_plot("Plot_Decompo.pdf",
#                    PLOT_ALL2, base_height = 9/cm(1),
#                    base_width = 20/cm(1), dpi = 610)


``` 




# 1. ANALYSIS VARIABILITY
## Length
```{r }

head(datamerged)
hist(datamerged$Length)
mod0 <- lmer(Length ~ Tpop:Predpop + Tpop + Predpop + (1|Pop), data = datamerged, 
      REML=FALSE) #To compare model

#hist(resid(mod0))
mod1 <- lmer(Length ~ Tpop + Predpop + (1|Pop), data = datamerged, 
      REML=FALSE) #To compare model

anova(mod0,mod1,test="Chisq") #Remove Interaction

mod2 <- lmer(Length ~ Predpop + (1|Pop), data = datamerged, 
      REML=FALSE) #To compare model
mod3 <- lmer(Length ~ Tpop + (1|Pop), data = datamerged, 
      REML=FALSE) #To compare model
anova(mod1,mod2,test="Chisq") #Remove Predpop
anova(mod1,mod3,test="Chisq") #Remove Tpop

modnull <- lmer(Length ~ 1 + (1|Pop), data = datamerged, 
      REML=FALSE) 
anova(modnull,mod2,test="Chisq") #Remove Predpop
anova(modnull,mod3,test="Chisq") #Remove Tpop


### MuMIn::r.squaredGLMM(modbest)
#Marginal R²: Variance explained by the fixed effect(s) only.
#Conditional R²: Variance explained by the entire model (fixed + random effects).
### r2glmm::r2beta(modbest, partial = TRUE)
#1.6% of the variance in Length is explained by TempExpNum (fixed effect).
#0% of the variance is additionally explained by the random effect Pop.
##summary(modbest)

tapply(datamerged$Length, datamerged$Pop, length)

# ####################################
# ############################ PREDICT 
# ####################################
# modbest <- lmer(Length ~ TempExpNum + (1|Pop), 
#                 data = datamerged, REML=TRUE) 
# 
# anova(modbest)
# 
# #dat_predict_length <- expand.grid(TempExpNum=values(datamerged$TempExpNum))
# dat_predict_length <- data.frame(TempExpNum=seq(min(datamerged$TempExpNum), 
#                                                 max(datamerged$TempExpNum), 0.1))
# 
# 
# #Predict
# dat_predict_length$predict <- predict(modbest, type = "response",  
#                                   re.form = NA,
#                                   newdata = dat_predict_length)
# 
# #Confidence interval
# bb <- lme4::bootMer(modbest,
#               FUN=function(x)predict(x, 
#                                      newdata = dat_predict_length,
#                                      re.form=NA),
#               nsim=5000)
# 
# # Take quantiles of predictions from bootstrap replicates.
# # These represent the confidence interval of the mean at any value of Time.
# dat_predict_length$CI_lower <- apply(bb$t, 2, quantile, 0.025)
# dat_predict_length$CI_upper <- apply(bb$t, 2, quantile, 0.975)
# 
# 
# ####################################
# ############################ PLOT 
# ####################################
# 
# PLOT_Length_predict <- ggplot(data = dat_predict_length,
#         aes(x = TempExpNum, y = predict)) + 
#   ggplot2::geom_ribbon(data = dat_predict_length, 
#                        aes(ymin = CI_lower, 
#                            ymax = CI_upper, 
#                            x = TempExpNum), 
#                        alpha = 0.1, size = 0.1) + 
#   geom_jitter(data = datamerged, 
#                        aes(x = TempExpNum, y = Length, 
#                            color = interaction(Predpop,Tpop), 
#                            shape = interaction(Predpop,Tpop)), 
#                        alpha = 0.8, size = 0.8) + 
#   geom_line(data = dat_predict_length,
#             aes(x = TempExpNum, 
#                 y = predict),
#             size = 1.5) + 
#   scale_shape_manual(name = "Evolution history",
#                     labels=c("Ctrl.Ambiant" = "Ambient x NoPred" ,
#                              "Pred.Ambiant" = "Ambient x Pred" ,
#                               "Ctrl.Warm" = "Warm x NoPred",
#                              "Pred.Warm" = "Warm x Pred" ),
#                     values = c(16,17,16,17)) +  
#   scale_color_manual(name = "Evolution history",
#                     labels=c("Ctrl.Ambiant" = "Ambient x NoPred" ,
#                              "Pred.Ambiant" = "Ambient x Pred" ,
#                               "Ctrl.Warm" = "Warm x NoPred",
#                              "Pred.Warm" = "Warm x Pred" ),
#                     values = c("#92c5de","#0571b0","#f4a582","#ca0020")) +
#   guides(shape = guide_legend(override.aes = list(size = 5))) +
#   xlab("Experimental temperature") +
#   ylab("Size") +
#   scale_x_continuous(breaks = datamerged$TempExpNum) +
#   theme_LO_sobre 
# PLOT_Length_predict
# 
# 
# # cowplot::save_plot("Plot_predict_size.pdf",
# #                    PLOT_Length_predict, base_height = 10/cm(1),
# #                    base_width = 15/cm(1), dpi = 610)
# 


```



## Body mass
```{r }

head(datamerged)
hist(datamerged$Mass_Ind)
mod0 <- lmer(Mass_Ind ~ Tpop:Predpop + Tpop + Predpop + (1|Pop), data = datamerged, 
      REML=FALSE) #To compare model

#hist(resid(mod0))
mod1 <- lmer(Mass_Ind ~ Tpop + Predpop + (1|Pop), data = datamerged, 
      REML=FALSE) #To compare model

anova(mod0,mod1,test="Chisq") #Remove Interaction

mod2 <- lmer(Mass_Ind ~ Predpop + (1|Pop), data = datamerged, 
      REML=FALSE) #To compare model
mod3 <- lmer(Mass_Ind ~ Tpop + (1|Pop), data = datamerged, 
      REML=FALSE) #To compare model
anova(mod1,mod2,test="Chisq") #Remove Predpop
anova(mod1,mod3,test="Chisq") #Remove Tpop

modnull <- lmer(Mass_Ind ~ 1 + (1|Pop), data = datamerged, 
      REML=FALSE) 
anova(modnull,mod2,test="Chisq") #Remove Predpop
anova(modnull,mod3,test="Chisq") #Remove Tpop


modnull <- lmer(Mass_Ind ~ 1 + (1|Pop), data = datamerged, 
      REML=TRUE) 
summary(modnull)
### MuMIn::r.squaredGLMM(modbest)
#Marginal R²: Variance explained by the fixed effect(s) only.
#Conditional R²: Variance explained by the entire model (fixed + random effects).
### r2glmm::r2beta(modbest, partial = TRUE)
#1.6% of the variance in Length is explained by TempExpNum (fixed effect).
#0% of the variance is additionally explained by the random effect Pop.
##summary(modbest)

tapply(datamerged$Mass_Ind, datamerged$Tpop, mean, na.rm=TRUE)

# ####################################
# ############################ PREDICT 
# ####################################
# modbest <- lmer(Length ~ TempExpNum + (1|Pop), 
#                 data = datamerged, REML=TRUE) 
# 
# anova(modbest)
# 
# #dat_predict_length <- expand.grid(TempExpNum=values(datamerged$TempExpNum))
# dat_predict_length <- data.frame(TempExpNum=seq(min(datamerged$TempExpNum), 
#                                                 max(datamerged$TempExpNum), 0.1))
# 
# 
# #Predict
# dat_predict_length$predict <- predict(modbest, type = "response",  
#                                   re.form = NA,
#                                   newdata = dat_predict_length)
# 
# #Confidence interval
# bb <- lme4::bootMer(modbest,
#               FUN=function(x)predict(x, 
#                                      newdata = dat_predict_length,
#                                      re.form=NA),
#               nsim=5000)
# 
# # Take quantiles of predictions from bootstrap replicates.
# # These represent the confidence interval of the mean at any value of Time.
# dat_predict_length$CI_lower <- apply(bb$t, 2, quantile, 0.025)
# dat_predict_length$CI_upper <- apply(bb$t, 2, quantile, 0.975)
# 
# 
# ####################################
# ############################ PLOT 
# ####################################
# 
# PLOT_Length_predict <- ggplot(data = dat_predict_length,
#         aes(x = TempExpNum, y = predict)) + 
#   ggplot2::geom_ribbon(data = dat_predict_length, 
#                        aes(ymin = CI_lower, 
#                            ymax = CI_upper, 
#                            x = TempExpNum), 
#                        alpha = 0.1, size = 0.1) + 
#   geom_jitter(data = datamerged, 
#                        aes(x = TempExpNum, y = Length, 
#                            color = interaction(Predpop,Tpop), 
#                            shape = interaction(Predpop,Tpop)), 
#                        alpha = 0.8, size = 0.8) + 
#   geom_line(data = dat_predict_length,
#             aes(x = TempExpNum, 
#                 y = predict),
#             size = 1.5) + 
#   scale_shape_manual(name = "Evolution history",
#                     labels=c("Ctrl.Ambiant" = "Ambient x NoPred" ,
#                              "Pred.Ambiant" = "Ambient x Pred" ,
#                               "Ctrl.Warm" = "Warm x NoPred",
#                              "Pred.Warm" = "Warm x Pred" ),
#                     values = c(16,17,16,17)) +  
#   scale_color_manual(name = "Evolution history",
#                     labels=c("Ctrl.Ambiant" = "Ambient x NoPred" ,
#                              "Pred.Ambiant" = "Ambient x Pred" ,
#                               "Ctrl.Warm" = "Warm x NoPred",
#                              "Pred.Warm" = "Warm x Pred" ),
#                     values = c("#92c5de","#0571b0","#f4a582","#ca0020")) +
#   guides(shape = guide_legend(override.aes = list(size = 5))) +
#   xlab("Experimental temperature") +
#   ylab("Size") +
#   scale_x_continuous(breaks = datamerged$TempExpNum) +
#   theme_LO_sobre 
# PLOT_Length_predict
# 
# 
# # cowplot::save_plot("Plot_predict_size.pdf",
# #                    PLOT_Length_predict, base_height = 10/cm(1),
# #                    base_width = 15/cm(1), dpi = 610)
# 


```



## Respiro
### AIC best model
```{r }
plot_rawdata <- ggplot() + 
  geom_jitter(data = datamerged_respiro, 
                       aes(x = TempExpNum, y = log(Slope_Pos), 
                           group = interaction(Predpop,Tpop),
                           color = interaction(Predpop,Tpop), 
                           shape = interaction(Predpop,Tpop)), 
                       alpha = 0.8, size = 0.8) + 
  scale_shape_manual(name = "Evolution history",
                    labels=c("Ctrl.Ambiant" = "Ambient x NoPred" ,
                             "Pred.Ambiant" = "Ambient x Pred" ,
                              "Ctrl.Warm" = "Warm x NoPred",
                             "Pred.Warm" = "Warm x Pred" ),
                    values = c(16,17,16,17)) +  
  scale_color_manual(name = "Evolution history",
                    labels=c("Ctrl.Ambiant" = "Ambient x NoPred" ,
                             "Pred.Ambiant" = "Ambient x Pred" ,
                              "Ctrl.Warm" = "Warm x NoPred",
                             "Pred.Warm" = "Warm x Pred" ),
                    values = c("#92c5de","#0571b0","#f4a582","#ca0020")) +
  guides(shape = guide_legend(override.aes = list(size = 5))) +
  xlab("Experimental temperature") +
  ylab("Log(Slope Respiro)") +
  scale_x_continuous(breaks = datamerged$TempExpNum) +
  theme_LO_sobre 
plot_rawdata


##### HERE ISSUE 
cols_needed <- c("Slope_Pos", "TempExpNum", "Mass_Ind", "Pop")
datamerged_respiro_clean <- datamerged_respiro[complete.cases(datamerged_respiro[, cols_needed]), ]







#Type of mod
ModSquare <- lmer(log(Slope_Pos) ~ TempExpNum + TempExpNumSquare + log(Mass_Ind) +  (1|Pop),
     data = datamerged_respiro_clean, REML=FALSE)

ModLinear <- lmer(log(Slope_Pos) ~ TempExpNum + log(Mass_Ind) + (1|Pop),
     data = datamerged_respiro_clean, REML=FALSE)

ModHetero <-  nlme::lme(fixed = log(Slope_Pos) ~ TempExpNum + log(Mass_Ind)  ,
  random = ~1 | Pop, weights = varPower(form = ~ TempExpNum), 
  data = datamerged_respiro_clean, method = "ML") 

ModSpine <- nlme::lme(log(Slope_Pos) ~  ns(TempExpNum, 3) + log(Mass_Ind),
  random = ~1 | Pop,
  weights = varPower(form = ~ TempExpNum), 
  data = datamerged_respiro_clean, method = "ML")

ModGam <- mgcv::gam(log(Slope_Pos) ~  s(TempExpNum, k=5) + log(Mass_Ind) +
                  s(Pop, bs="re"), method = 'ML', 
                data=datamerged_respiro_clean)

ModNull <- lm(log(Slope_Pos) ~ 1,
     data = datamerged_respiro_clean)

AIC(ModLinear,ModHetero,ModSpine,ModSquare, ModGam, ModNull)

#For predictions
ModGam <- mgcv::gam(log(Slope_Pos) ~  s(TempExpNum, k=5) + #log(Mass_Ind) +
                  s(Pop, bs="re"), method = 'ML', 
                data=datamerged_respiro_clean)



########## ADD PREDICTIONS

#Make prediction grid
newdat <- data.frame(TempExpNum = seq(min(datamerged$TempExpNum),
                                      max(datamerged$TempExpNum),
                                      length.out = 100), 
                     Mass_Ind = mean(datamerged_respiro_clean$Mass_Ind))
newdat$TempExpNumSquare <- newdat$TempExpNum*newdat$TempExpNum
#Get predictions
newdat$Linear <- predict(ModLinear, newdata = newdat, re.form = NA)
newdat$Square <- predict(ModSquare, newdata = newdat, re.form = NA)
newdat$Hetero <- predict(ModHetero, newdata = newdat, level = 0)
newdat$Spine  <- predict(ModSpine,  newdata = newdat, level = 0)
newdat$Null  <- predict(ModNull,  newdata = newdat, level = 0)

predictGAM <- tidymv::get_gam_predictions(model = ModGam,
                                       series = TempExpNum,
                                       #exclude_terms = 'log(Mass_Ind)',
                                       exclude_random = TRUE)
predictGAM$Model <- "Gamm"
predictGAM$Fit <- predictGAM$`log(Slope_Pos)`

# 3. Reshape for ggplot
pred_long <- reshape(newdat,
  varying = names(newdat)[-1],   # all columns except TempExpNum
  v.names = "Fit",
  timevar = "Model",
  times = names(newdat)[-1],
  direction = "long")


pred_long <- pred_long[pred_long$Model!="Mass_Ind",]
pred_long <- pred_long[pred_long$Model!="TempExpNumSquare",]

pred_long <- rbind(pred_long[,c(1,2,3)],
      predictGAM[,c(1,8,9)])



# 4. Add lines to your existing plot
plot_allmodels <- plot_rawdata +
  facet_wrap(~ Model, nrow = 1) +
  geom_line(data = pred_long,
            aes(x = TempExpNum, y = Fit),
            size = 1.2)
plot_allmodels



############# BEST MODEL SPINES 

ModSpine <- nlme::lme(log(Slope_Pos) ~  ns(TempExpNum, 3) ,
  random = ~1 | Pop,
  weights = varPower(form = ~ TempExpNum), 
  data = datamerged_respiro_clean, method = "ML")


ModSpineHetero <- nlme::lme(log(Slope_Pos) ~  ns(TempExpNum, 3) ,
  random = ~1 | Pop,
  data = datamerged_respiro_clean, method = "ML")

AIC(ModSpineHetero,ModSpine)


############# BEST MODEL SPINES with Hetero

# cowplot::save_plot("Plot_All_Models_Respiro.pdf",
#                    plot_allmodels, base_height = 10/cm(1),
#                    base_width = 40/cm(1), dpi = 610)


```










### Splines Nlmer - USED
```{r }
### Non-linear model WITHOUT random effects, using LRT

ModSpine <- nlme::lme(log(Slope_Pos) ~  ns(TempExpNum, 3) + log(Mass_Ind),
  random = ~1 | Pop,
  weights = varPower(form = ~ TempExpNum), 
  data = datamerged_respiro_clean, method = "ML")


#library(splines)

nlme_model <- lme(
  log(Slope_Pos) ~ ns(TempExpNum, 3) * Tpop * Predpop + log(Mass_Ind),
  random = ~1 | Pop,
  weights = varPower(form = ~ TempExpNum),  # variance croît avec TempExpNum
  data = datamerged_respiro_clean,
  method = "ML"
)


nlme_0 <- lme(
  log(Slope_Pos)  ~ ns(TempExpNum, 3):Tpop:Predpop + 
    ns(TempExpNum, 3):Tpop + ns(TempExpNum, 3):Predpop + Tpop:Predpop + 
    ns(TempExpNum, 3) + Tpop + Predpop + log(Mass_Ind),
  random = ~1 | Pop,
    weights = varPower(form = ~ TempExpNum),  # variance croît avec TempExpNum
data = datamerged_respiro_clean,
  method = "ML"
)
nlme_1 <- lme(
  log(Slope_Pos)  ~  ns(TempExpNum, 3):Tpop + ns(TempExpNum, 3):Predpop + Tpop:Predpop + 
    ns(TempExpNum, 3) + Tpop + Predpop + log(Mass_Ind) ,
  random = ~1 | Pop,
    weights = varPower(form = ~ TempExpNum),  # variance croît avec TempExpNum
data = datamerged_respiro_clean,
  method = "ML")


anova(nlme_1,nlme_0) # remove interaction 


nlme_4 <- lme(log(Slope_Pos)  ~  ns(TempExpNum, 3):Predpop + Tpop:Predpop + 
    ns(TempExpNum, 3) + Tpop + Predpop + log(Mass_Ind),
  random = ~1 | Pop,
    weights = varPower(form = ~ TempExpNum),  # variance croît avec TempExpNum
data = datamerged_respiro_clean,
  method = "ML")

nlme_2 <- lme(log(Slope_Pos)  ~  ns(TempExpNum, 3):Tpop  + Tpop:Predpop + 
    ns(TempExpNum, 3) + Tpop + Predpop + log(Mass_Ind) ,
  random = ~1 | Pop,
    weights = varPower(form = ~ TempExpNum),  # variance croît avec TempExpNum
data = datamerged_respiro_clean,
  method = "ML")

nlme_3 <- lme(log(Slope_Pos)  ~  ns(TempExpNum, 3):Tpop + ns(TempExpNum, 3):Predpop  + 
    ns(TempExpNum, 3) + Tpop + Predpop + log(Mass_Ind) ,
  random = ~1 | Pop,
    weights = varPower(form = ~ TempExpNum),  # variance croît avec TempExpNum
data = datamerged_respiro_clean,
  method = "ML")
anova(nlme_1,nlme_2) # remove interaction 
anova(nlme_1,nlme_3) # remove interaction 
anova(nlme_1,nlme_4) # remove interaction 



nlme_4 <- lme(log(Slope_Pos)  ~  ns(TempExpNum, 3) + Tpop + Predpop + log(Mass_Ind),
  random = ~1 | Pop,
  weights = varPower(form = ~ TempExpNum),  # variance croît avec TempExpNum
  data = datamerged_respiro_clean,
  method = "ML")

nlme_5 <- lme(log(Slope_Pos)  ~ Tpop + Predpop + log(Mass_Ind) ,
  random = ~1 | Pop,
  weights = varPower(form = ~ TempExpNum),  # variance croît avec TempExpNum
  data = datamerged_respiro_clean,
  method = "ML")

nlme_6 <- lme(log(Slope_Pos)  ~  ns(TempExpNum, 3) + Predpop + log(Mass_Ind),
  random = ~1 | Pop,
  weights = varPower(form = ~ TempExpNum),  # variance croît avec TempExpNum
  data = datamerged_respiro_clean,
  method = "ML")

nlme_7 <- lme(log(Slope_Pos)  ~  ns(TempExpNum, 3) + Tpop + log(Mass_Ind),
  random = ~1 | Pop,
    weights = varPower(form = ~ TempExpNum),  # variance croît avec TempExpNum
data = datamerged_respiro_clean,
  method = "ML")
anova(nlme_5,nlme_4) # keep ns(TempExpNum, 3) 
anova(nlme_6,nlme_4) # remove Tpop 
anova(nlme_7,nlme_4) # remove Predpop 



nlme_7 <- lme(log(Slope_Pos)  ~  ns(TempExpNum, 3) + log(Mass_Ind),
  random = ~1 | Pop,
  weights = varPower(form = ~ TempExpNum),  # variance croît avec TempExpNum
  data = datamerged_respiro_clean,
  method = "ML")

nlme_8 <- lme(log(Slope_Pos)  ~  log(Mass_Ind) ,
  random = ~1 | Pop,
  weights = varPower(form = ~ TempExpNum) ,  # variance croît avec TempExpNum
  data = datamerged_respiro_clean,
  method = "ML")
anova(nlme_7,nlme_8, test = "Chisq") # keep ns(TempExpNum, 3) 

#Check covariate Mass_ind
nlme_8 <- lme(log(Slope_Pos)  ~  ns(TempExpNum, 3)  ,
  random = ~1 | Pop,
  weights = varPower(form = ~ TempExpNum) ,  # variance croît avec TempExpNum
  data = datamerged_respiro_clean,
  method = "ML")
anova(nlme_7,nlme_8) # keep log(Mass_Ind)


#Double check heteroscedasticity
nlme_best <- lme(log(Slope_Pos)  ~  ns(TempExpNum, 3) + log(Mass_Ind) ,
  random = ~1 | Pop,
    weights = varPower(form = ~ TempExpNum),  # variance croît avec TempExpNum
data = datamerged_respiro_clean,
  method = "ML")
nlme_best2 <- lme(log(Slope_Pos)  ~  ns(TempExpNum, 3) + log(Mass_Ind),
  random = ~1 | Pop,
data = datamerged_respiro_clean,
  method = "ML")
anova(nlme_best2,nlme_best) # keep varPower(form = ~ TempExpNum)



### Doublecheck spines 
nlme_9 <- lme(log(Slope_Pos)  ~  ns(TempExpNum, 3) + log(Mass_Ind),
  random = ~1 | Pop,
  weights = varPower(form = ~ TempExpNum),  # variance croît avec TempExpNum
  data = datamerged_respiro_clean,
  method = "ML")
nlme_10 <- lme(log(Slope_Pos)  ~  ns(TempExpNum, 2) + log(Mass_Ind),
  random = ~1 | Pop,
  weights = varPower(form = ~ TempExpNum),  # variance croît avec TempExpNum
  data = datamerged_respiro_clean,
  method = "ML")
anova(nlme_9,nlme_10) # keep log(Mass_Ind)


nlme_best <- lme(log(Slope_Pos)  ~  ns(TempExpNum, 3) + log(Mass_Ind),
  random = ~1 | Pop,
  weights = varPower(form = ~ TempExpNum),  # variance croît avec TempExpNum
  data = datamerged_respiro_clean,
  method = "REML")

summary(nlme_best)

var(resid(nlme_best))
sqrt(var(resid(nlme_best)))

#####################################################################
##################### PREDICTIONS ###################################

### BEST MODEL
nlme_best <- lme(log(Slope_Pos)  ~  ns(TempExpNum, 3)  + log(Mass_Ind),
  random = ~1 | Pop,
  weights = varPower(form = ~ TempExpNum),  # variance croît avec TempExpNum
  data = datamerged_respiro_clean,
  method = "REML")

#Slope_Corrected_ij=β_0+β_1B_1(TempExpNum_ij)+β_2B_2(TempExpNum_ij)+β_3B_3(TempExpNum_ij)+u_j+ε_ij 
#B_1, B_2, B_3 = fonctions de base du spline naturel générées par ns(TempExpNum, 3)
#β_0,β_1,β_2,β_3= coefficients fixes (estimés par lme)
#u_j∼N(0,σ_u2)u_j \sim N(0, \sigma^2_u)u_j∼N(0,σ_u2) = effet aléatoire de la population Pop
#ε_ij = erreur résiduelle avec variance qui dépend de TempExpNum (grâce à varPower)

summary(nlme_best)
var(residuals(nlme_best))


#Predict dataset
dat_predict_respiro <- data.frame(TempExpNum = seq(min(datamerged_respiro_clean$TempExpNum),
                                      max(datamerged_respiro_clean$TempExpNum),
                                      length.out = 10), 
                     Mass_Ind = mean(datamerged_respiro_clean$Mass_Ind))

# Buildd the design matrix
X <- model.matrix(formula(nlme_best)[-2], dat_predict_respiro)


#extract fixed effects
fixef <- fixed.effects(nlme_best)
fixed_pred <- as.vector(X %*% fixef)

#Random effects
sd_pop <- as.numeric(VarCorr(nlme_best)[1, "StdDev"])
sd_resid <- nlme_best$sigma

# Number of simulations
nsim <- 5000



pred_boot <- matrix(NA, nrow = nrow(dat_predict_respiro), ncol = nsim)

pops <- unique(datamerged_respiro_clean$Pop)

for(i in 1:nsim){
  # residuals (heteroscedasticity is modeled via varPower, ideally we should scale resid by fitted values, but here we keep it simple)
  resid_sim <- rnorm(nrow(dat_predict_respiro), 0, sd_resid)
  
  # total prediction = fixed + random + residual
  lp <- fixed_pred  + resid_sim
  pred_boot[, i] <- lp
}

# 95% CI
# dat_predict_respiro$CI_lower <- apply(pred_boot, 1, quantile, 0.025)
# dat_predict_respiro$CI_upper <- apply(pred_boot, 1, quantile, 0.975)



## Estimate 
dat_predict_respiro$predict <- predict(nlme_best, newdata = dat_predict_respiro, level = 0)
dat_predict_respiro$CI_lower <- apply(pred_boot, 1, quantile, 0.025)
dat_predict_respiro$CI_upper <- apply(pred_boot, 1, quantile, 0.975)

dat_predict_respiro[which.max(dat_predict_respiro$predict), ]
dat_predict_respiro[which.min(dat_predict_respiro$predict), ]

####################################
############################ PLOT 
####################################


plot_predict_respiro <- ggplot(data = dat_predict_respiro,
        aes(x = TempExpNum, y = predict)) + 
  ggplot2::geom_ribbon(data = dat_predict_respiro, 
                       aes(ymin = CI_lower, 
                           ymax = CI_upper, 
                           x = TempExpNum), 
                       alpha = 0.1, size = 0.1) + 
  geom_jitter(data = datamerged_respiro_clean, 
                       aes(x = TempExpNum, y = log(Slope_Pos), 
                           color = interaction(Predpop,Tpop), 
                           shape = interaction(Predpop,Tpop)), 
                       alpha = 0.8, size = 0.8) + 
  geom_line(data = dat_predict_respiro,
            aes(x = TempExpNum, 
                y = predict),
            size = 1.5) + 
  scale_shape_manual(name = "Evolutionary conditions",
                    labels=c("Ctrl.Ambiant" = "Ambient x Control" ,
                             "Pred.Ambiant" = "Ambient x Predator" ,
                              "Ctrl.Warm" = "Warm x Control",
                             "Pred.Warm" = "Warm x Predator" ),
                    values = c(16,17,16,17)) +  
  scale_color_manual(name = "Evolutionary conditions",
                    labels=c("Ctrl.Ambiant" = "Ambient x Control" ,
                             "Pred.Ambiant" = "Ambient x Predator" ,
                              "Ctrl.Warm" = "Warm x Control",
                             "Pred.Warm" = "Warm x Predator" ),
                    values = c("#92c5de","#0571b0","#f4a582","#ca0020")) +
 scale_fill_manual(name = "Evolutionary conditions",
                    labels=c("Ctrl.Ambiant" = "Ambient x Control" ,
                             "Pred.Ambiant" = "Ambient x Predator" ,
                              "Ctrl.Warm" = "Warm x Control",
                             "Pred.Warm" = "Warm x Predator" ),
                    values = c("#92c5de","#0571b0","#f4a582","#ca0020")) +
  guides(shape = guide_legend(override.aes = list(size = 5))) +
  xlab("Test temperature") +
  ylab("Metabolic rate") +
  scale_x_continuous(breaks = datamerged$TempExpNum) +
  theme_LO_sobre 
plot_predict_respiro

# # 
cowplot::save_plot("Plot_Fig2_predict_respiro_nLMER.pdf",
                   plot_predict_respiro, base_height = 10/cm(1),
                   base_width = 15/cm(1), dpi = 610)


```











### lmer - NOT USED
```{r }

hist(datamerged$Slope_Corrected)

mod0 <- lmer(Slope_Corrected ~ TempExpNum:Tpop:Predpop + 
     Tpop:Predpop + TempExpNum:Predpop + TempExpNum:Tpop + 
     TempExpNum + Tpop + Predpop + (1|Pop), data = datamerged, 
      REML=FALSE) #To compare model

#hist(resid(mod0))
mod1 <- lmer(Slope_Corrected ~ Tpop:Predpop + TempExpNum:Predpop + TempExpNum:Tpop + 
     TempExpNum + Tpop + Predpop  +  (1|Pop), data = datamerged, 
      REML=FALSE) #To compare model
anova(mod0,mod1,test="Chisq") #Remove Interaction triple

mod2 <- lmer(Slope_Corrected ~ Tpop:Predpop + TempExpNum:Tpop + 
     TempExpNum + Tpop + Predpop  + (1|Pop), data = datamerged, 
      REML=FALSE) #To compare model
mod3 <- lmer(Slope_Corrected ~ Tpop:Predpop + TempExpNum:Predpop + 
     TempExpNum + Tpop + Predpop  + (1|Pop), data = datamerged, 
      REML=FALSE) #To compare model
anova(mod1,mod2,test="Chisq") #Remove Interaction with TempExpNum
anova(mod1,mod3,test="Chisq") #Remove Interaction with TempExpNum


mod4 <- lmer(Slope_Corrected ~ Tpop:Predpop + 
     TempExpNum + Tpop + Predpop  + (1|Pop), data = datamerged, 
      REML=FALSE) 
mod5 <- lmer(Slope_Corrected ~   TempExpNum + Tpop + Predpop  + (1|Pop), 
             data = datamerged, 
      REML=FALSE) 
anova(mod4,mod5,test="Chisq") #Remove Interactionn Tpop Predpop

mod6 <- lmer(Slope_Corrected ~ Tpop + Predpop  +  (1|Pop), 
             data = datamerged, REML=FALSE) 
anova(mod5,mod6,test="Chisq") #Keep TempExpNum

mod7 <- lmer(Slope_Corrected ~ TempExpNum + Tpop  + (1|Pop), data = datamerged, 
      REML=FALSE) 
anova(mod5,mod7,test="Chisq") #Remove Predpop

mod8 <- lmer(Slope_Corrected ~ TempExpNum  + Predpop   + (1|Pop), data = datamerged, 
      REML=FALSE) 
anova(mod4,mod8,test="Chisq") #Remove Tpop



modbest <- lmer(Slope_Corrected ~ TempExpNum + (1|Pop), data = datamerged, REML=FALSE) 

MuMIn::r.squaredGLMM(modbest)
#Marginal R²: Variance explained by the fixed effect(s) only.
#Conditional R²: Variance explained by the entire model (fixed + random effects).
#r2glmm::r2beta(modbest, partial = TRUE)
#X% of the variance in Length is explained by TempExpNum (fixed effect).
#X% of the variance is additionally explained by the random effect Pop.
summary(modbest)

####################################
############################ PREDICT 
####################################
modbest <- lmer(Slope_Corrected ~ TempExpNum  +  (1|Pop), 
     data = datamerged, REML=TRUE) 



anova(modbest)
summary(modbest)

dat_predict_respiro <- expand.grid(TempExpNum = seq(min(datamerged$TempExpNum),
                                                  max(datamerged$TempExpNum), 0.1))

dat_predict_respiro$TempExpNumSquare <- dat_predict_respiro$TempExpNum * dat_predict_respiro$TempExpNum

#Predict
dat_predict_respiro$predict <- predict(modbest, type = "response",  
                                  re.form = NA,
                                  newdata = dat_predict_respiro)

#Confidence interval
bb <- lme4::bootMer(modbest,
              FUN=function(x)predict(x, 
                                     newdata = dat_predict_respiro,
                                     re.form=NA),
              nsim=500)

# Take quantiles of predictions from bootstrap replicates.
# These represent the confidence interval of the mean at any value of Time.
dat_predict_respiro$CI_lower <- apply(bb$t, 2, quantile, 0.025)
dat_predict_respiro$CI_upper <- apply(bb$t, 2, quantile, 0.975)



####################################
############################ PLOT 
####################################

plot_predict_respiro <- ggplot(data = dat_predict_respiro,
        aes(x = TempExpNum, y = predict)) + 
  ggplot2::geom_ribbon(data = dat_predict_respiro, 
                       aes(ymin = CI_lower, 
                           ymax = CI_upper, 
                           x = TempExpNum), 
                       alpha = 0.1, size = 0.1) + 
  geom_jitter(data = datamerged, 
                       aes(x = TempExpNum, y = Slope, 
                           color = interaction(Predpop,Tpop), 
                           shape = interaction(Predpop,Tpop)), 
                       alpha = 0.8, size = 0.8) + 
  geom_line(data = dat_predict_respiro,
            aes(x = TempExpNum, 
                y = predict),
            size = 1.5) + 
  scale_shape_manual(name = "Evolution history",
                    labels=c("Ctrl.Ambiant" = "Ambient x NoPred" ,
                             "Pred.Ambiant" = "Ambient x Pred" ,
                              "Ctrl.Warm" = "Warm x NoPred",
                             "Pred.Warm" = "Warm x Pred" ),
                    values = c(16,17,16,17)) +  
  scale_color_manual(name = "Evolution history",
                    labels=c("Ctrl.Ambiant" = "Ambient x NoPred" ,
                             "Pred.Ambiant" = "Ambient x Pred" ,
                              "Ctrl.Warm" = "Warm x NoPred",
                             "Pred.Warm" = "Warm x Pred" ),
                    values = c("#92c5de","#0571b0","#f4a582","#ca0020")) +
 scale_fill_manual(name = "Evolution history",
                    labels=c("Ctrl.Ambiant" = "Ambient x NoPred" ,
                             "Pred.Ambiant" = "Ambient x Pred" ,
                              "Ctrl.Warm" = "Warm x NoPred",
                             "Pred.Warm" = "Warm x Pred" ),
                    values = c("#92c5de","#0571b0","#f4a582","#ca0020")) +
  guides(shape = guide_legend(override.aes = list(size = 5))) +
  xlab("Experimental temperature") +
  ylab("Slope Respiro") +
  scale_x_continuous(breaks = datamerged$TempExpNum) +
  theme_LO_sobre 
plot_predict_respiro

# 
# cowplot::save_plot("Plot_predict_respiro_LMER.pdf",
#                    plot_predict_respiro, base_height = 10/cm(1),
#                    base_width = 15/cm(1), dpi = 610)

```


### Heteroscedasticity nlmer - NOT USED - OLD
```{r }

mod0_nlme <- lme(
  fixed = Slope_Corrected ~ TempExpNum * Tpop * Predpop,
  random = ~1 | Pop,
  weights = varPower(form = ~ TempExpNum),  # variance croît avec TempExpNum
  data = datamerged,
  method = "ML")




##Test variance

## Clean data: remove rows with missing values in relevant columns
datamerged_clean <- datamerged[complete.cases(datamerged[, 
  c("Slope_Corrected", "TempExpNum", "Tpop", "Predpop", "Pop")]), ]

## Base model (homoscedastic residuals)
mod0_homo <- lme(
  fixed = Slope_Corrected ~ TempExpNum * Tpop * Predpop,
  random = ~1 | Pop,
  data   = datamerged_clean,
  method = "ML"
)

## Variance grows with TempExpNum (power function)
mod0_power <- update(mod0_homo,
  weights = varPower(form = ~ TempExpNum)
)

## Variance grows with TempExpNum (exponential function)
mod0_exp <- update(mod0_homo,
  weights = varExp(form = ~ TempExpNum)
)

## Variances differ by Tpop
mod0_ident <- update(mod0_homo,
  weights = varIdent(form = ~ 1 | Tpop)
)

## Compare models
anova(mod0_homo, mod0_power, mod0_exp, mod0_ident)

## Optional: inspect residuals for best model
plot(mod0_power, resid(., type="pearson") ~ fitted(.), abline=0)



#hist(resid(mod0))


## LRT 
mod0 <- lme(fixed = Slope_Corrected ~ Tpop:Predpop:TempExpNum + Tpop:Predpop + TempExpNum:Predpop + TempExpNum:Tpop + TempExpNum + Tpop + Predpop,
  random = ~1 | Pop,
  weights = varPower(form = ~ TempExpNum),  # variance croît avec TempExpNum
  data = datamerged,
  method = "ML")
 
 mod1 <- lme(fixed = Slope_Corrected ~ Tpop:Predpop + TempExpNum:Predpop + TempExpNum:Tpop + TempExpNum + Tpop + Predpop,
  random = ~1 | Pop,
  weights = varPower(form = ~ TempExpNum),  # variance croît avec TempExpNum
  data = datamerged,
  method = "ML")
anova(mod0,mod1) #Remove Interaction triple


mod2 <- lme(fixed = Slope_Corrected ~  TempExpNum:Predpop + TempExpNum:Tpop + TempExpNum + Tpop + Predpop,
  random = ~1 | Pop,
  weights = varPower(form = ~ TempExpNum),  # variance croît avec TempExpNum
  data = datamerged,
  method = "ML")
mod3 <- lme(fixed = Slope_Corrected ~ Tpop:Predpop + TempExpNum:Tpop + TempExpNum + Tpop + Predpop,
  random = ~1 | Pop,
  weights = varPower(form = ~ TempExpNum),  # variance croît avec TempExpNum
  data = datamerged,
  method = "ML")
mod4 <- lme(fixed = Slope_Corrected ~ Tpop:Predpop + TempExpNum:Predpop + TempExpNum + Tpop + Predpop,
  random = ~1 | Pop,
  weights = varPower(form = ~ TempExpNum),  # variance croît avec TempExpNum
  data = datamerged,
  method = "ML")
anova(mod1,mod2) #Remove Interaction 
anova(mod1,mod3) #Remove Interaction 
anova(mod1,mod4) #Remove Interaction 



mod5 <- lme(fixed = Slope_Corrected ~ TempExpNum + Tpop + Predpop,
  random = ~1 | Pop, weights = varPower(form = ~ TempExpNum), data = datamerged, method = "ML")
anova(mod4,mod5) #Remove Interactionn Tpop Predpop

mod6 <- lme(fixed = Slope_Corrected ~  Tpop + Predpop,
  random = ~1 | Pop, weights = varPower(form = ~ TempExpNum), data = datamerged, method = "ML")
anova(mod5,mod6) #Keep TempExpNum

mod7 <- lme(fixed = Slope_Corrected ~ TempExpNum  + Predpop,
  random = ~1 | Pop, weights = varPower(form = ~ TempExpNum), data = datamerged, method = "ML")
anova(mod5,mod7) #Remove Predpop

mod8 <- lme(fixed = Slope_Corrected ~ TempExpNum + Tpop ,
  random = ~1 | Pop, weights = varPower(form = ~ TempExpNum), data = datamerged, method = "ML")
anova(mod5,mod8) #Remove Tpop



modbest <- lme(fixed = Slope_Corrected ~ TempExpNum ,
  random = ~1 | Pop, weights = varPower(form = ~ TempExpNum), data = datamerged, method = "ML") 

MuMIn::r.squaredGLMM(modbest)
#Marginal R²: Variance explained by the fixed effect(s) only.
#Conditional R²: Variance explained by the entire model (fixed + random effects).
#r2glmm::r2beta(modbest, partial = TRUE)
#X% of the variance in Length is explained by TempExpNum (fixed effect).
#X% of the variance is additionally explained by the random effect Pop.
summary(modbest)

####################################
############################ PREDICT 
####################################
modbest <-  lme(fixed = Slope_Corrected ~ TempExpNum ,
  random = ~1 | Pop, weights = varPower(form = ~ TempExpNum), data = datamerged, method = "REML") 

anova(modbest)
summary(modbest)

dat_predict_respiro <- expand.grid(TempExpNum = seq(min(datamerged$TempExpNum),
                                                  max(datamerged$TempExpNum), 1))

#Predict
dat_predict_respiro$predict <- predict(modbest, 
                                  newdata = dat_predict_respiro, level = 0)

#Confidence interval
# Prepare new data for predictions (fixed effect only)
nsim <- 50000
pred_boot <- matrix(NA, nrow = nrow(dat_predict_respiro), ncol = nsim)
fixef <- fixed.effects(modbest)   # fixed effect coefficients

# Random intercept SD
sd_pop <- as.numeric(VarCorr(modbest)[1, "StdDev"])

# Residual SD (sigma)
sd_resid <- modbest$sigma

ranef_sd <- c(sd_pop, sd_resid)


for(i in 1:nsim){
  # Sample random intercepts for each Pop
  pop_re <- rnorm(length(unique(datamerged_clean$Pop)), 0, ranef_sd[1])
  names(pop_re) <- unique(datamerged_clean$Pop)
  
  # Simulate residuals
  resid_sim <- rnorm(nrow(dat_predict_respiro), 0, ranef_sd[2])
  
  # Linear predictor: fixed effects only (no weights)
  lp <- fixef[1] + fixef[2]*dat_predict_respiro$TempExpNum + resid_sim
  pred_boot[,i] <- lp
}

# Confidence intervals
ci_lower <- apply(pred_boot, 1, quantile, 0.025)
ci_upper <- apply(pred_boot, 1, quantile, 0.975)
dat_predict_respiro$CI_lower <- ci_lower
dat_predict_respiro$CI_upper <- ci_upper



####################################
############################ PLOT 
####################################

View(datamerged)

plot_predict_respiro <- ggplot(data = dat_predict_respiro,
        aes(x = TempExpNum, y = predict)) + 
  ggplot2::geom_ribbon(data = dat_predict_respiro, 
                       aes(ymin = CI_lower, 
                           ymax = CI_upper, 
                           x = TempExpNum), 
                       alpha = 0.1, size = 0.1) + 
  geom_jitter(data = datamerged, 
                       aes(x = TempExpNum, y = Slope, 
                           color = interaction(Predpop,Tpop), 
                           shape = interaction(Predpop,Tpop)), 
                       alpha = 0.8, size = 0.8) + 
  geom_line(data = dat_predict_respiro,
            aes(x = TempExpNum, 
                y = predict),
            size = 1.5) + 
  scale_shape_manual(name = "Evolution history",
                    labels=c("Ctrl.Ambiant" = "Ambient x NoPred" ,
                             "Pred.Ambiant" = "Ambient x Pred" ,
                              "Ctrl.Warm" = "Warm x NoPred",
                             "Pred.Warm" = "Warm x Pred" ),
                    values = c(16,17,16,17)) +  
  scale_color_manual(name = "Evolution history",
                    labels=c("Ctrl.Ambiant" = "Ambient x NoPred" ,
                             "Pred.Ambiant" = "Ambient x Pred" ,
                              "Ctrl.Warm" = "Warm x NoPred",
                             "Pred.Warm" = "Warm x Pred" ),
                    values = c("#92c5de","#0571b0","#f4a582","#ca0020")) +
 scale_fill_manual(name = "Evolution history",
                    labels=c("Ctrl.Ambiant" = "Ambient x NoPred" ,
                             "Pred.Ambiant" = "Ambient x Pred" ,
                              "Ctrl.Warm" = "Warm x NoPred",
                             "Pred.Warm" = "Warm x Pred" ),
                    values = c("#92c5de","#0571b0","#f4a582","#ca0020")) +
  guides(shape = guide_legend(override.aes = list(size = 5))) +
  xlab("Experimental temperature") +
  ylab("Slope Respiro") +
  scale_x_continuous(breaks = datamerged$TempExpNum) +
  theme_LO_sobre 
plot_predict_respiro

# 
# cowplot::save_plot("Plot_predict_respiro_LMER.pdf",
#                    plot_predict_respiro, base_height = 10/cm(1),
#                    base_width = 15/cm(1), dpi = 610)

```




### Quadratic nlmer - NOT USED - A finir OLD
```{r }
### Non-linear model WITHOUT random effects, using LRT
mod <- lm(Slope_Corrected ~ TempExpNum*Pop + TempExpNumSquare*Pop, data = datamerged)
newdat <- expand.grid(TempExpNum = seq(min(datamerged$TempExpNum),
                                      max(datamerged$TempExpNum),
                                      length.out = 100), 
                     Pop = unique(levels(datamerged$Pop)))
newdat$TempExpNumSquare <- newdat$TempExpNum*newdat$TempExpNum
newdat$Linear <- predict(mod, newdata = newdat, re.form = NA)

# plot_rawdata + geom_line(data = newdat, 
#                          aes(x = TempExpNum, y = Linear, group = Pop))
# 


nlme_model <- lme(
  Slope_Corrected ~ TempExpNumSquare * Tpop * Predpop,
  random = ~1 | Pop,
    weights = varPower(form = ~ TempExpNum),  # variance croît avec TempExpNum
  data = datamerged,
  method = "ML"
)


nlme_0 <- lme(
  Slope_Corrected ~ TempExpNumSquare:Tpop:Predpop + 
   TempExpNumSquare:Tpop + TempExpNumSquare:Predpop + Tpop:Predpop + 
   TempExpNumSquare + TempExpNumSquare + Tpop + Predpop ,
  random = ~1 | Pop,
    weights = varPower(form = ~ TempExpNum),  # variance croît avec TempExpNum
data = datamerged,
  method = "ML"
)
nlme_1 <- lme(
  Slope_Corrected ~  TempExpNumSquare:Tpop + TempExpNumSquare:Predpop + Tpop:Predpop + 
    TempExpNumSquare + Tpop + Predpop ,
  random = ~1 | Pop,
    weights = varPower(form = ~ TempExpNum),  # variance croît avec TempExpNum
data = datamerged,
  method = "ML"
)


anova(nlme_1,nlme_0) # remove interaction 


nlme_4 <- lme(
  Slope_Corrected ~  TempExpNumSquare:Predpop + Tpop:Predpop + 
    TempExpNumSquare + Tpop + Predpop ,
  random = ~1 | Pop,
    weights = varPower(form = ~ TempExpNum),  # variance croît avec TempExpNum
data = datamerged,
  method = "ML"
)
nlme_2 <- lme(
  Slope_Corrected ~ TempExpNumSquare:Tpop  + Tpop:Predpop + 
    TempExpNumSquare + Tpop + Predpop ,
  random = ~1 | Pop,
    weights = varPower(form = ~ TempExpNum),  # variance croît avec TempExpNum
data = datamerged,
  method = "ML"
)
nlme_3 <- lme(Slope_Corrected ~  TempExpNumSquare:Tpop + TempExpNumSquare:Predpop  + 
  TempExpNumSquare + Tpop + Predpop ,
  random = ~1 | Pop,
    weights = varPower(form = ~ TempExpNum),  # variance croît avec TempExpNum
data = datamerged,
  method = "ML")
anova(nlme_1,nlme_2) # remove interaction 
anova(nlme_1,nlme_3) # remove interaction 
anova(nlme_1,nlme_4) # remove interaction 

nlme_5 <- lme(Slope_Corrected ~ Tpop + Predpop ,
  random = ~1 | Pop,
    weights = varPower(form = ~ TempExpNum),  # variance croît avec TempExpNum
data = datamerged,
  method = "ML")

nlme_6 <- lme(Slope_Corrected ~  TempExpNumSquare + Predpop ,
  random = ~1 | Pop,
    weights = varPower(form = ~ TempExpNum),  # variance croît avec TempExpNum
data = datamerged,
  method = "ML")

nlme_7 <- lme(Slope_Corrected ~ TempExpNumSquare + Tpop ,
  random = ~1 | Pop,
    weights = varPower(form = ~ TempExpNum),  # variance croît avec TempExpNum
data = datamerged,
  method = "ML")
anova(nlme_5,nlme_4) # keep TempExpNumSquare 
anova(nlme_6,nlme_4) # remove Tpop 
anova(nlme_7,nlme_4) # remove Predpop 



nlme_7 <- lme(Slope_Corrected ~  TempExpNumSquare ,
  random = ~1 | Pop,
    weights = varPower(form = ~ TempExpNum),  # variance croît avec TempExpNum
data = datamerged,
  method = "ML")
nlme_8 <- lme(Slope_Corrected ~  1 ,
  random = ~1 | Pop,
    weights = varPower(form = ~ TempExpNum),  # variance croît avec TempExpNum
data = datamerged,
  method = "ML")
anova(nlme_7,nlme_8) # keep TempExpNumSquare



nlme_best <- lme(Slope_Corrected ~  TempExpNumSquare ,
  random = ~1 | Pop,
  weights = varPower(form = ~ TempExpNum),  # variance croît avec TempExpNum
  data = datamerged,
  method = "ML")

summary(nlme_best)

#Check
nlme_best <- lme(Slope_Corrected ~  TempExpNumSquare,
  random = ~1 | Pop,
    weights = varPower(form = ~ TempExpNum),  # variance croît avec TempExpNum
data = datamerged,
  method = "ML")
nlme_best2 <- lme(Slope_Corrected ~  TempExpNumSquare ,
  random = ~1 | Pop,
data = datamerged,
  method = "ML")
anova(nlme_best2,nlme_best) # keep varPower(form = ~ TempExpNum)




# Number of simulations
nsim <- 5000  # try smaller first, then increase if it works

# Extract fixed effects
fixef <- fixed.effects(nlme_best)

# Random + residual SDs
sd_pop <- as.numeric(VarCorr(nlme_best)[1, "StdDev"])
sd_resid <- nlme_best$sigma

# Fixed-effect design matrix for prediction dataset
X <- model.matrix(formula(nlme_best)[-2], dat_predict_respiro) 
# (-2 drops the response, leaves rhs)

# Compute fixed-effect prediction
fixed_pred <- as.vector(X %*% fixef)

# Storage for bootstrapped sims
pred_boot <- matrix(NA, nrow = nrow(dat_predict_respiro), ncol = nsim)

for(i in 1:nsim){
  # Random intercepts for populations
  pop_re <- rnorm(length(unique(datamerged$Pop)), 0, sd_pop)
  names(pop_re) <- unique(datamerged$Pop)
  
  resid_sim <- rnorm(nrow(dat_predict_respiro), 0, sd_resid)
  
  # Prediction = fixed + random + residual
  lp <- fixed_pred  + resid_sim
  pred_boot[, i] <- lp
}

# 95% CI
dat_predict_respiro$CI_lower <- apply(pred_boot, 1, quantile, 0.025)
dat_predict_respiro$CI_upper <- apply(pred_boot, 1, quantile, 0.975)

####################################
############################ PLOT 
####################################


plot_predict_respiro <- ggplot(data = dat_predict_respiro,
        aes(x = TempExpNum, y = predict)) + 
  ggplot2::geom_ribbon(data = dat_predict_respiro, 
                       aes(ymin = CI_lower, 
                           ymax = CI_upper, 
                           x = TempExpNum), 
                       alpha = 0.1, size = 0.1) + 
  geom_jitter(data = datamerged, 
                       aes(x = TempExpNum, y = Slope, 
                           color = interaction(Predpop,Tpop), 
                           shape = interaction(Predpop,Tpop)), 
                       alpha = 0.8, size = 0.8) + 
  geom_line(data = dat_predict_respiro,
            aes(x = TempExpNum, 
                y = predict),
            size = 1.5) + 
  scale_shape_manual(name = "Evolution history",
                    labels=c("Ctrl.Ambiant" = "Ambient x NoPred" ,
                             "Pred.Ambiant" = "Ambient x Pred" ,
                              "Ctrl.Warm" = "Warm x NoPred",
                             "Pred.Warm" = "Warm x Pred" ),
                    values = c(16,17,16,17)) +  
  scale_color_manual(name = "Evolution history",
                    labels=c("Ctrl.Ambiant" = "Ambient x NoPred" ,
                             "Pred.Ambiant" = "Ambient x Pred" ,
                              "Ctrl.Warm" = "Warm x NoPred",
                             "Pred.Warm" = "Warm x Pred" ),
                    values = c("#92c5de","#0571b0","#f4a582","#ca0020")) +
 scale_fill_manual(name = "Evolution history",
                    labels=c("Ctrl.Ambiant" = "Ambient x NoPred" ,
                             "Pred.Ambiant" = "Ambient x Pred" ,
                              "Ctrl.Warm" = "Warm x NoPred",
                             "Pred.Warm" = "Warm x Pred" ),
                    values = c("#92c5de","#0571b0","#f4a582","#ca0020")) +
  guides(shape = guide_legend(override.aes = list(size = 5))) +
  xlab("Experimental temperature") +
  ylab("Respirometry rate") +
  scale_x_continuous(breaks = datamerged$TempExpNum) +
  theme_LO_sobre 
plot_predict_respiro

# 
# cowplot::save_plot("Plot_predict_respiro_nLMER.pdf",
#                    plot_predict_respiro, base_height = 10/cm(1),
#                    base_width = 15/cm(1), dpi = 610)


```


### Gamm Model of Slope corrected by weight in the dataset - NOT USED  - OLD
```{r }

####################################
############################ MODEL GAMM 
####################################



## Voir pour un modele GAMM ! 
m0 <- mgcv::gam(Slope ~ EvolHistory + Mass_Ind + 
                  s(TempExpNum, k=5) +
                  s(TempExpNum, by= EvolHistory, k=5) + 
                  s(Pop, bs="re"), method = 'ML', 
                data=datamerged_subset)
m1 <- mgcv::gam(Slope ~ EvolHistory + Mass_Ind + 
                  s(TempExpNum, k=5) +
                  s(Pop, bs="re"), method = 'ML', 
                data=datamerged_subset)

itsadug::compareML(m0,m1,suggest.report = TRUE) #remove Interaction


m2 <- mgcv::gam(Slope ~ Mass_Ind + 
                  s(TempExpNum, k=5) +
                  s(Pop, bs="re"), method = 'ML', 
                data=datamerged_subset)
itsadug::compareML(m1,m2,suggest.report = TRUE) #remove Evolve History


m3 <- mgcv::gam(Slope ~ Mass_Ind + TempExpNum + 
                  s(Pop, bs="re"), method = 'ML', 
                data=datamerged_subset)
itsadug::compareML(m2,m3,suggest.report = TRUE) #Keep smooth TempExpNum

m4 <- mgcv::gam(Slope ~ s(TempExpNum, k=5) +
                  s(Pop, bs="re"), method = 'ML', 
                data=datamerged_subset)
itsadug::compareML(m4,m2,suggest.report = TRUE) #Keep Mass



m5 <- mgcv::gam(Slope ~ Mass_Ind + 
                  s(TempExpNum, k=5) , method = 'ML', 
                data=datamerged_subset)
itsadug::compareML(m5,m2,suggest.report = TRUE) #Keep Pop random effect



## Best model: m2 
mbest <- mgcv::gam(Slope ~ Mass_Ind + 
                  s(TempExpNum, k=5) +
                  s(Pop, bs="re"), method = 'ML', 
                data=datamerged_subset)

summary(mbest)
mgcv::summary.gam(mbest)

mbestpred <- mgcv::gam(Slope ~  s(TempExpNum, k=5) +
                  s(Pop, bs="re"), method = 'ML', 
                data=datamerged_subset)

mod_Best_p <- tidymv::get_gam_predictions(model = mbestpred,
                                       series = TempExpNum,
                                       exclude_random = TRUE)

# tidymv::plot_smooths(mbestpred, TempExpNum, 
#                      exclude_random = TRUE)



    

plot_predict_respiro <- ggplot(data = mod_Best_p,
        aes(x = TempExpNum, y = Slope)) + 
  ggplot2::geom_ribbon(data = mod_Best_p, 
                       aes(ymin = CI_lower, 
                           ymax = CI_upper, 
                           x = TempExpNum), 
                       alpha = 0.1, size = 0.1) + 
  geom_jitter(data = datamerged_subset, 
                       aes(x = TempExpNum, y = Slope, 
                           group = interaction(Predpop,Tpop),
                           color = interaction(Predpop,Tpop), 
                           shape = interaction(Predpop,Tpop)), 
                       alpha = 0.8, size = 0.8) + 
  geom_line(data = mod_Best_p,
            aes(x = TempExpNum, 
                y = Slope),
            size = 1.5) + 
  scale_shape_manual(name = "Evolution history",
                    labels=c("Ctrl.Ambiant" = "Ambient x NoPred" ,
                             "Pred.Ambiant" = "Ambient x Pred" ,
                              "Ctrl.Warm" = "Warm x NoPred",
                             "Pred.Warm" = "Warm x Pred" ),
                    values = c(16,17,16,17)) +  
  scale_color_manual(name = "Evolution history",
                    labels=c("Ctrl.Ambiant" = "Ambient x NoPred" ,
                             "Pred.Ambiant" = "Ambient x Pred" ,
                              "Ctrl.Warm" = "Warm x NoPred",
                             "Pred.Warm" = "Warm x Pred" ),
                    values = c("#92c5de","#0571b0","#f4a582","#ca0020")) +
 scale_fill_manual(name = "Evolution history",
                    labels=c("Ctrl.Ambiant" = "Ambient x NoPred" ,
                             "Pred.Ambiant" = "Ambient x Pred" ,
                              "Ctrl.Warm" = "Warm x NoPred",
                             "Pred.Warm" = "Warm x Pred" ),
                    values = c("#92c5de","#0571b0","#f4a582","#ca0020")) +
  guides(shape = guide_legend(override.aes = list(size = 5))) +
  xlab("Experimental temperature") +
  ylab("Slope Respiro") +
  scale_x_continuous(breaks = datamerged$TempExpNum) +
  theme_LO_sobre 
plot_predict_respiro

# cowplot::save_plot("Plot_predict_respiro_GAMM.pdf",
#                    plot_predict_respiro, base_height = 10/cm(1),
#                    base_width = 15/cm(1), dpi = 610)

```


## Decompo
### Raffard reference: -log(Rate) USED
```{r }
mod0 <- lmer(Deg_Rate_Raffard ~ TempExpNum:Tpop:Predpop + 
     Tpop:Predpop + TempExpNum:Predpop + TempExpNum:Tpop + 
     TempExpNum + Tpop + Predpop + (1|Pop), 
     data = data_decompo_clean, 
      REML=FALSE) #To compare model

#hist(resid(mod0))
mod1 <- lmer(Deg_Rate_Raffard ~ 
     Tpop:Predpop + TempExpNum:Predpop + TempExpNum:Tpop + 
     TempExpNum + Tpop + Predpop + (1|Pop), 
     data = data_decompo_clean, 
      REML=FALSE) #To compare model

anova(mod0,mod1,test="Chisq") #Remove Interaction

mod2 <- lmer(Deg_Rate_Raffard ~ 
     TempExpNum:Predpop + TempExpNum:Tpop + 
     TempExpNum + Tpop + Predpop + (1|Pop), 
     data = data_decompo_clean, 
      REML=FALSE) #To compare model
mod3 <- lmer(Deg_Rate_Raffard ~ 
     Tpop:Predpop  + TempExpNum:Tpop + 
     TempExpNum + Tpop + Predpop + (1|Pop), 
     data = data_decompo_clean, 
      REML=FALSE) #To compare model
mod4 <- lmer(Deg_Rate_Raffard ~ 
     Tpop:Predpop + TempExpNum:Predpop +  
     TempExpNum + Tpop + Predpop + (1|Pop), 
     data = data_decompo_clean, 
      REML=FALSE) #To compare model
anova(mod1,mod2,test="Chisq") #Remove Tpop:Predpop
anova(mod1,mod4,test="Chisq") #Keep: TempExpNum:Tpop
anova(mod1,mod3,test="Chisq") #Keep: TempExpNum:Predpop

mod5 <- lmer(Deg_Rate_Raffard ~ TempExpNum:Predpop + TempExpNum:Tpop + 
     TempExpNum + Tpop + Predpop + (1|Pop), 
     data = data_decompo_clean, 
      REML=FALSE) #To compare model
mod6 <- lmer(Deg_Rate_Raffard ~ TempExpNum:Predpop + TempExpNum + Tpop + Predpop + (1|Pop), 
     data = data_decompo_clean, 
      REML=FALSE) #To compare model
mod7 <- lmer(Deg_Rate_Raffard ~ TempExpNum:Tpop + TempExpNum + Tpop + Predpop + (1|Pop), 
     data = data_decompo_clean, 
      REML=FALSE) #To compare model
anova(mod5,mod6,test="Chisq") #Keep:TempExpNum:Tpop
anova(mod5,mod7,test="Chisq") #Keep:TempExpNum:Tpop





## BEST MODEL 
modbest <- lmer(Deg_Rate_Raffard ~  TempExpNum:Predpop + TempExpNum:Tpop + 
     TempExpNum + Tpop + Predpop  + (1|Pop), 
     data = data_decompo_clean) #To compare model
summary(modbest)
# Obtain slopes of TempExpNum for all combinations of Predpop and Tpop
slopes <- emmeans::emtrends(modbest, ~ Predpop + Tpop, var = "TempExpNum")
summary(slopes)


MuMIn::r.squaredGLMM(modbest)
#Marginal R²: Variance explained by the fixed effect(s) only.
#Conditional R²: Variance explained by the entire model (fixed + random effects).
r2glmm::r2beta(modbest, partial = TRUE)
#1.6% of the variance in Length is explained by TempExpNum (fixed effect).
#0% of the variance is additionally explained by the random effect Pop.
summary(modbest)

tapply(data_decompo_clean$Deg_Rate_Raffard, data_decompo_clean$Pop, mean)
tapply(data_decompo_clean$Deg_Rate_Raffard, data_decompo_clean$EvolHistory, mean)


# ####################################
# ############################ PREDICT 
# ####################################
anova(modbest)
## BEST MODEL 
modbest <- lmer(Deg_Rate_Raffard ~  TempExpNum:Predpop + TempExpNum:Tpop + 
     TempExpNum + Tpop + Predpop  + (1|Pop), 
     data = data_decompo_clean) #To compare model
summary(modbest)
# Obtain slopes of TempExpNum for all combinations of Predpop and Tpop
slopes <- emmeans::emtrends(modbest, ~ Predpop + Tpop, var = "TempExpNum")
summary(slopes)



dat_predict_decompo <-expand.grid(TempExpNum=seq(min(
  data_decompo_clean$TempExpNum),
  max(data_decompo_clean$TempExpNum), 1),
                                   Tpop = unique(data_decompo_clean$Tpop),
                                   Predpop = unique(data_decompo_clean$Predpop))



#Predict
dat_predict_decompo$predict <- predict(modbest, type = "response",
                                  re.form = NA,
                                  newdata = dat_predict_decompo)

#Confidence interval
bb <- lme4::bootMer(modbest,
              FUN=function(x)predict(x,
                                     newdata = dat_predict_decompo,
                                     re.form=NA),
              nsim=5000)

# Take quantiles of predictions from bootstrap replicates.
# These represent the confidence interval of the mean at any value of Time.
dat_predict_decompo$CI_lower <- apply(bb$t, 2, quantile, 0.025)
dat_predict_decompo$CI_upper <- apply(bb$t, 2, quantile, 0.975)


dat_predict_decompo[dat_predict_decompo$TempExpNum==27,]

## PLOT


plot_predict_decompo <- ggplot(data = dat_predict_decompo,
        aes(x = TempExpNum, y = predict, group = interaction(Predpop,Tpop))) +
  ggplot2::geom_ribbon(data = dat_predict_decompo,
                       aes(ymin = CI_lower,
                           ymax = CI_upper,
                           x = TempExpNum,
                           color = interaction(Predpop,Tpop),
                           fill = interaction(Predpop,Tpop),
                           group = interaction(Predpop,Tpop)),
                       alpha = 0.1, size = 0.05) +
  geom_jitter(data = data_decompo_clean,
                       aes(x = TempExpNum, y = Deg_Rate_Raffard,
                           color = interaction(Predpop,Tpop),
                           shape = interaction(Predpop,Tpop)),
                       alpha = 0.8, size = 1.2, position = position_dodge(width = 1)) +
  geom_line(data = dat_predict_decompo,
            aes(x = TempExpNum,
                y = predict,
                group = interaction(Predpop,Tpop),
                linetype = interaction(Predpop,Tpop),
                color = interaction(Predpop,Tpop)),
            size = 1) +
  scale_shape_manual(name = "Evolutionary conditions",
                    labels=c("Ctrl.Ambiant" = "Ambient x Control" ,
                             "Pred.Ambiant" = "Ambient x Predator" ,
                              "Ctrl.Warm" = "Warm x Control",
                             "Pred.Warm" = "Warm x Predator" ),
                    values = c(16,17,16,17)) +
  scale_linetype_manual(name = "Evolutionary conditions",
                    labels=c("Ctrl.Ambiant" = "Ambient x Control" ,
                             "Pred.Ambiant" = "Ambient x Predator" ,
                              "Ctrl.Warm" = "Warm x Control",
                             "Pred.Warm" = "Warm x Predator"),
                    values = c("dashed","dashed","solid","solid")) +
  scale_color_manual(name = "Evolutionary conditions",
                    labels=c("Ctrl.Ambiant" = "Ambient x Control" ,
                             "Pred.Ambiant" = "Ambient x Predator" ,
                              "Ctrl.Warm" = "Warm x Control",
                             "Pred.Warm" = "Warm x Predator" ),
                    values = c("#92c5de","#0571b0","#f4a582","#ca0020")) +
 scale_fill_manual(name = "Evolutionary conditions",
                    labels=c("Ctrl.Ambiant" = "Ambient x Control" ,
                             "Pred.Ambiant" = "Ambient x Predator" ,
                              "Ctrl.Warm" = "Warm x Control",
                             "Pred.Warm" = "Warm x Predator" ),
                    values = c("#92c5de","#0571b0","#f4a582","#ca0020")) +
  guides(shape = guide_legend(override.aes = list(size = 5))) +
  xlab("Test temperature") +
  ylab("Decomposition rate") +
  scale_x_continuous(breaks = data_decompo_clean$TempExpNum) +
  theme_LO_sobre
plot_predict_decompo
# 
 
# ####################################
# ############################ PLOT 
# ####################################
# 

# 
# cowplot::save_plot("Plot_Fig4_predict_Decompo_Raffard.pdf",
#                    plot_predict_decompo, base_height = 10/cm(1),
#                    base_width = 15/cm(1), dpi = 610)



```







### Decompo Azelles normalized - NOT USED
```{r }
mod0 <- lme4::glmer( Deg_Rate_Norm ~ TempExpNum:Tpop:Predpop + 
     Tpop:Predpop + TempExpNum:Predpop + TempExpNum:Tpop + 
     TempExpNum + Tpop + Predpop + (1|Pop), family = binomial(link="logit"),
     data = data_decompo_clean) 

#boundary (singular) fit: see ?isSingular
summary(mod0)
head(data_decompo_clean) #No variance explained by Pop -> REMOVED!

mod0 <- glm(Deg_Rate_Norm ~ TempExpNum:Tpop:Predpop + 
     Tpop:Predpop + TempExpNum:Predpop + TempExpNum:Tpop + 
     TempExpNum + Tpop + Predpop, family = binomial(link="logit"),
     data = data_decompo_clean) 


#Check for  overdispersion 
summary(mod0)
0.84315/108
# No issue of overdispersion

mod0 <- glm( Deg_Rate_Norm ~ TempExpNum:Tpop:Predpop + 
     Tpop:Predpop + TempExpNum:Predpop + TempExpNum:Tpop + 
     TempExpNum + Tpop + Predpop, family = binomial(link="logit"),
     data = data_decompo_clean) 
summary(mod0)


#Model selection 
mod1 <- glm(Deg_Rate_Norm ~ 
     Tpop:Predpop + TempExpNum:Predpop + TempExpNum:Tpop + 
     TempExpNum + Tpop + Predpop, family = binomial(link="logit"),
     data = data_decompo_clean) 
anova(mod0,mod1,test="Chisq") #remove triple interaction



mod2 <- glm(Deg_Rate_Norm ~ 
     TempExpNum:Predpop + TempExpNum:Tpop + 
     TempExpNum + Tpop + Predpop , family = binomial(link="logit"),
     data = data_decompo_clean) 
mod3 <- glm(Deg_Rate_Norm ~ 
     Tpop:Predpop  + TempExpNum:Tpop + 
     TempExpNum + Tpop + Predpop , family = binomial(link="logit"),
     data = data_decompo_clean) 
mod4 <- glm(Deg_Rate_Norm ~ 
     Tpop:Predpop + TempExpNum:Predpop + 
     TempExpNum + Tpop + Predpop , family = binomial(link="logit"),
     data = data_decompo_clean) 

anova(mod2,mod1,test="Chisq") #remove  interaction
anova(mod3,mod1,test="Chisq") #remove  interaction
anova(mod4,mod1,test="Chisq") #remove  interaction

mod5 <- glm(Deg_Rate_Norm ~ TempExpNum + Tpop + Predpop, 
            family = binomial(link="logit"),
     data = data_decompo_clean) 
anova(mod4,mod5,test="Chisq") #Keep simplest model with no-interaction


mod6 <- glm(Deg_Rate_Norm ~  Tpop + Predpop, 
            family = binomial(link="logit"),
     data = data_decompo_clean) 
mod7 <- glm(Deg_Rate_Norm ~ TempExpNum  + Predpop, 
            family = binomial(link="logit"),
     data = data_decompo_clean) 
mod8 <- glm(Deg_Rate_Norm ~ TempExpNum + Tpop , 
            family = binomial(link="logit"),
     data = data_decompo_clean) 
anova(mod6,mod5,test="Chisq") #Remove all effects
anova(mod7,mod5,test="Chisq") #Remove all effects
anova(mod8,mod5,test="Chisq") #Remove all effects

mod9 <- glm(Deg_Rate_Norm ~ 1, 
            family = binomial(link="logit"),
     data = data_decompo_clean)
anova(mod9,mod8,test="Chisq") #Remove everything!! Weird 

```

### Decompo Azelles - NOT USED
```{r }


mod0 <- lme4::glmer( Deg_Rate ~ TempExpNum:Tpop:Predpop + 
     Tpop:Predpop + TempExpNum:Predpop + TempExpNum:Tpop + 
     TempExpNum + Tpop + Predpop + (1|Pop), family = binomial(link="logit"),
     data = data_decompo_clean) 

#boundary (singular) fit: see ?isSingular
summary(mod0) #No variance explained by Pop -> REMOVED!

mod0 <- glm(Deg_Rate ~ TempExpNum:Tpop:Predpop + 
     Tpop:Predpop + TempExpNum:Predpop + TempExpNum:Tpop + 
     TempExpNum + Tpop + Predpop, family = binomial(link="logit"),
     data = data_decompo_clean) 


#Check for  overdispersion 
summary(mod0)
0.46712/108
# No issue of overdispersion

mod0 <- glm(Deg_Rate ~ TempExpNum:Tpop:Predpop + 
     Tpop:Predpop + TempExpNum:Predpop + TempExpNum:Tpop + 
     TempExpNum + Tpop + Predpop, family = binomial(link="logit"),
     data = data_decompo_clean) 
summary(mod0)


#Model selection 
mod1 <- glm(Deg_Rate ~ 
     Tpop:Predpop + TempExpNum:Predpop + TempExpNum:Tpop + 
     TempExpNum + Tpop + Predpop, family = binomial(link="logit"),
     data = data_decompo_clean) 
anova(mod0,mod1,test="Chisq") #remove triple interaction



mod2 <- glm(Deg_Rate ~ 
     TempExpNum:Predpop + TempExpNum:Tpop + 
     TempExpNum + Tpop + Predpop , family = binomial(link="logit"),
     data = data_decompo_clean) 
mod3 <- glm(Deg_Rate ~ 
     Tpop:Predpop  + TempExpNum:Tpop + 
     TempExpNum + Tpop + Predpop , family = binomial(link="logit"),
     data = data_decompo_clean) 
mod4 <- glm(Deg_Rate ~ 
     Tpop:Predpop + TempExpNum:Predpop + 
     TempExpNum + Tpop + Predpop , family = binomial(link="logit"),
     data = data_decompo_clean) 

anova(mod2,mod1,test="Chisq") #remove  interaction
anova(mod3,mod1,test="Chisq") #remove  interaction
anova(mod4,mod1,test="Chisq") #remove  interaction

mod5 <- glm(Deg_Rate ~ TempExpNum + Tpop + Predpop, 
            family = binomial(link="logit"),
     data = data_decompo_clean) 
anova(mod4,mod5,test="Chisq") #Keep simplest model with no-interaction


mod6 <- glm(Deg_Rate ~  Tpop + Predpop, 
            family = binomial(link="logit"),
     data = data_decompo_clean) 
mod7 <- glm(Deg_Rate ~ TempExpNum  + Predpop, 
            family = binomial(link="logit"),
     data = data_decompo_clean) 
mod8 <- glm(Deg_Rate ~ TempExpNum + Tpop , 
            family = binomial(link="logit"),
     data = data_decompo_clean) 
anova(mod6,mod5,test="Chisq") #Remove all effects
anova(mod7,mod5,test="Chisq") #Remove all effects
anova(mod8,mod5,test="Chisq") #Remove all effects

mod9 <- glm(Deg_Rate ~ 1, 
            family = binomial(link="logit"),
     data = data_decompo_clean)
anova(mod9,mod8,test="Chisq") #Remove everything!! Weird 

```




### Logit Decompo Azelles - NOT USED
```{r }

data_decompo_clean$Logit <- log((data_decompo_clean$Deg_Rate/(1-data_decompo_clean$Deg_Rate)))
  
mod0 <- lmer( Logit ~ TempExpNum:Tpop:Predpop + 
     Tpop:Predpop + TempExpNum:Predpop + TempExpNum:Tpop + 
     TempExpNum + Tpop + Predpop + (1|Pop),
     data = data_decompo_clean) 


#Model selection 
mod0 <- lmer( Logit ~ TempExpNum:Tpop:Predpop + 
     Tpop:Predpop + TempExpNum:Predpop + TempExpNum:Tpop + 
     TempExpNum + Tpop + Predpop + (1|Pop),
     data = data_decompo_clean) 

mod1 <- lmer(Logit ~ 
     Tpop:Predpop + TempExpNum:Predpop + TempExpNum:Tpop + 
     TempExpNum + Tpop + Predpop + (1|Pop),
     data = data_decompo_clean) 
anova(mod0,mod1,test="Chisq") #remove triple interaction



mod2 <- lmer(Logit ~ 
     TempExpNum:Predpop + TempExpNum:Tpop + 
     TempExpNum + Tpop + Predpop + (1|Pop),
     data = data_decompo_clean) 
mod3 <- lmer(Logit ~ 
     Tpop:Predpop  + TempExpNum:Tpop + 
     TempExpNum + Tpop + Predpop + (1|Pop) ,
     data = data_decompo_clean) 
mod4 <- lmer(Logit ~ 
     Tpop:Predpop + TempExpNum:Predpop + 
     TempExpNum + Tpop + Predpop + (1|Pop),
     data = data_decompo_clean) 

anova(mod2,mod1,test="Chisq") #remove  interaction Tpop:Predpop
anova(mod3,mod1,test="Chisq") #KEEP  interaction
anova(mod4,mod1,test="Chisq") #KEEP  interaction

mod2 <- lmer(Logit ~ 
     TempExpNum:Predpop + TempExpNum:Tpop + 
     TempExpNum + Tpop + Predpop + (1|Pop),
     data = data_decompo_clean) 
mod5 <- lmer(Logit ~ TempExpNum:Tpop + TempExpNum + Tpop + Predpop + (1|Pop), 
     data = data_decompo_clean) 
mod5bis <- lmer(Logit ~ TempExpNum:Predpop + TempExpNum + Tpop + Predpop + (1|Pop), 
     data = data_decompo_clean) 
anova(mod2,mod5,test="Chisq") #Keep interaction
anova(mod2,mod5bis,test="Chisq") #Keep interaction



#Best model: 
modbest <- lmer(Logit ~ 
     TempExpNum:Predpop + TempExpNum:Tpop + 
     TempExpNum + Tpop + Predpop +  (1|Pop),
     data = data_decompo_clean) 

# emmeans::emmeans(modbest, list(pairwise ~ Tpop:Predpop), 
#                  adjust = "tukey") 

###################### 
###################### PREDICT 
###################### 
# dat_predict_decompo <- expand.grid(TempExpNum=seq(min(data_decompo_clean$TempExpNum),
#                                                   max(data_decompo_clean$TempExpNum), 1), 
#                                    Tpop = unique(data_decompo_clean$Tpop),
#                                    Predpop = unique(data_decompo_clean$Predpop))
# 
# 
# 
# #Predict
# dat_predict_decompo$predict <- predict(modbest, type = "response",  
#                                   re.form = NA,
#                                   newdata = dat_predict_decompo)
# 
# #Confidence interval
# bb <- lme4::bootMer(modbest,
#               FUN=function(x)predict(x, 
#                                      newdata = dat_predict_decompo,
#                                      re.form=NA),
#               nsim=500)
# 
# # Take quantiles of predictions from bootstrap replicates.
# # These represent the confidence interval of the mean at any value of Time.
# dat_predict_decompo$CI_lower <- apply(bb$t, 2, quantile, 0.025)
# dat_predict_decompo$CI_upper <- apply(bb$t, 2, quantile, 0.975)
# 
# 
# 
# 
# plot_predict_decompo <- ggplot(data = dat_predict_decompo,
#         aes(x = TempExpNum, y = predict, group = interaction(Predpop,Tpop))) + 
#   ggplot2::geom_ribbon(data = dat_predict_decompo, 
#                        aes(ymin = CI_lower, 
#                            ymax = CI_upper, 
#                            x = TempExpNum, 
#                            color = interaction(Predpop,Tpop),
#                            fill = interaction(Predpop,Tpop),
#                            group = interaction(Predpop,Tpop)), 
#                        alpha = 0.1, size = 0.1) + 
#   geom_jitter(data = data_decompo_clean, 
#                        aes(x = TempExpNum, y = Logit, 
#                            color = interaction(Predpop,Tpop), 
#                            shape = interaction(Predpop,Tpop)), 
#                        alpha = 0.8, size = 1.2, position = position_dodge(width = 1)) + 
#   geom_line(data = dat_predict_decompo,
#             aes(x = TempExpNum, 
#                 y = predict, 
#                 group = interaction(Predpop,Tpop),
#                 #linetype = interaction(Predpop,Tpop),
#                 color = interaction(Predpop,Tpop)),
#             size = 1) + 
#   scale_shape_manual(name = "Evolution history",
#                     labels=c("Ctrl.Ambiant" = "Ambient x NoPred" ,
#                              "Pred.Ambiant" = "Ambient x Pred" ,
#                               "Ctrl.Warm" = "Warm x NoPred",
#                              "Pred.Warm" = "Warm x Pred" ),
#                     values = c(16,17,16,17)) + 
#   # scale_linetype_manual(name = "Evolution history ",
#   #                   labels=c("Ctrl.Ambiant" = "Ambient x NoPred" ,
#   #                            "Pred.Ambiant" = "Ambient x Pred" ,
#   #                             "Ctrl.Warm" = "Warm x NoPred",
#   #                            "Pred.Warm" = "Warm x Pred" ),
#   #                   values = c("dashed","solid","dashed","solid")) + 
#   scale_color_manual(name = "Evolution history",
#                     labels=c("Ctrl.Ambiant" = "Ambient x NoPred" ,
#                              "Pred.Ambiant" = "Ambient x Pred" ,
#                               "Ctrl.Warm" = "Warm x NoPred",
#                              "Pred.Warm" = "Warm x Pred" ),
#                     values = c("#92c5de","#0571b0","#f4a582","#ca0020")) +
#  scale_fill_manual(name = "Evolution history",
#                     labels=c("Ctrl.Ambiant" = "Ambient x NoPred" ,
#                              "Pred.Ambiant" = "Ambient x Pred" ,
#                               "Ctrl.Warm" = "Warm x NoPred",
#                              "Pred.Warm" = "Warm x Pred" ),
#                     values = c("#92c5de","#0571b0","#f4a582","#ca0020")) +
#   guides(shape = guide_legend(override.aes = list(size = 5))) +
#   xlab("Experimental temperature") +
#   ylab("Logit Decompo Rate") +
#   scale_x_continuous(breaks = data_decompo_clean$TempExpNum) +
#   theme_LO_sobre 
# plot_predict_decompo
# 
# 
# # cowplot::save_plot("Plot_predict_logitrate.pdf",
# #                    plot_predict_decompo, base_height = 10/cm(1),
# #                    base_width = 15/cm(1), dpi = 610)

```





### Logit Decompo Azelles vs Control - NOT USED 
```{r }

data_decompo_clean_withcontrol$Logit <- log((data_decompo_clean_withcontrol$Deg_Rate/(1-data_decompo_clean_withcontrol$Deg_Rate)))

data_decompo_clean_withcontrol$Control<- ifelse(data_decompo_clean_withcontrol$EvolHistory=="C_C",
                                                "NoAzelles",
                                                "Azelles")


mod0 <- lmer( Logit ~ TempExpNum:EvolHistory + 
     EvolHistory + TempExpNum + (1|Pop),
     data = data_decompo_clean_withcontrol) 

mod1 <- lmer( Logit ~ TempExpNum:Control + 
     EvolHistory + TempExpNum + (1|Pop),
     data = data_decompo_clean_withcontrol) 
anova(mod0,mod1,test="Chisq") #Keep interaction


#Best model: 
modbest <-lmer( Logit ~ TempExpNum:EvolHistory + 
     EvolHistory + TempExpNum + (1|Pop),
     data = data_decompo_clean_withcontrol) 
summary(modbest)

#Slope:                               Estimate 
#TempExpNum                          0.028598   0.003762   7.602
#TempExpNum:EvolHistoryCtrl_Ambiant  0.015382   0.005076   3.030
#TempExpNum:EvolHistoryCtrl_Warm     0.027109   0.006037   4.490
#TempExpNum:EvolHistoryPred_Ambiant  0.009260   0.005030   1.841
#TempExpNum:EvolHistoryPred_Warm     0.012273   0.005387   2.278

emmeans::emmeans(modbest, list(pairwise ~ EvolHistory), 
                 adjust = "tukey") 

###################### 
###################### PREDICT 
###################### 
dat_predict_decompo <- expand.grid(
  TempExpNum=seq(min(data_decompo_clean_withcontrol$TempExpNum),
                 max(data_decompo_clean_withcontrol$TempExpNum), 1),
  EvolHistory = unique(data_decompo_clean_withcontrol$EvolHistory))



#Predict
dat_predict_decompo$predict <- predict(modbest, type = "response",  
                                  re.form = NA,
                                  newdata = dat_predict_decompo)

#Confidence interval
bb <- lme4::bootMer(modbest,
              FUN=function(x)predict(x, 
                                     newdata = dat_predict_decompo,
                                     re.form=NA),
              nsim=500)

# Take quantiles of predictions from bootstrap replicates.
# These represent the confidence interval of the mean at any value of Time.
dat_predict_decompo$CI_lower <- apply(bb$t, 2, quantile, 0.025)
dat_predict_decompo$CI_upper <- apply(bb$t, 2, quantile, 0.975)

###################### 
###################### PLOT 
###################### 


plot_predict_decompo <- ggplot(data = dat_predict_decompo,
        aes(x = TempExpNum, y = predict, group = EvolHistory)) + 
  ggplot2::geom_ribbon(data = dat_predict_decompo, 
                       aes(ymin = CI_lower, 
                           ymax = CI_upper, 
                           x = TempExpNum, 
                           color = EvolHistory,
                           fill = EvolHistory,
                           group = EvolHistory), 
                       alpha = 0.1, size = 0.1) + 
  geom_jitter(data = data_decompo_clean_withcontrol, 
                       aes(x = TempExpNum, y = Logit, 
                           color =EvolHistory, 
                           shape = EvolHistory), 
                       alpha = 0.8, size = 1.2, position = position_dodge(width = 1)) + 
  geom_line(data = dat_predict_decompo,
            aes(x = TempExpNum, 
                y = predict, 
                group = EvolHistory,
                #linetype = interaction(Predpop,Tpop),
                color = EvolHistory),
            size = 1) + 
  scale_shape_manual(name = "Evolution history",
                    labels=c("C_C" = "Control",
                             "Ctrl_Ambiant" = "Ambient x NoPred" ,
                             "Pred_Ambiant" = "Ambient x Pred" ,
                              "Ctrl_Warm" = "Warm x NoPred",
                             "Pred_Warm" = "Warm x Pred" ),
                    values = c(15,16,17,16,17)) +
  # scale_linetype_manual(name = "Evolution history ",
  #                   labels=c("Ctrl.Ambiant" = "Ambient x NoPred" ,
  #                            "Pred.Ambiant" = "Ambient x Pred" ,
  #                             "Ctrl.Warm" = "Warm x NoPred",
  #                            "Pred.Warm" = "Warm x Pred" ),
  #                   values = c("dashed","solid","dashed","solid")) + 
  scale_color_manual(name = "Evolution history",
                    labels=c("C_C" = "Control",
                             "Ctrl_Ambiant" = "Ambient x NoPred" ,
                              "Ctrl_Warm" = "Warm x NoPred",
                             "Pred_Ambiant" = "Ambient x Pred" ,
                             "Pred_Warm" = "Warm x Pred" ),
                    values = c("black","#92c5de","#f4a582","#0571b0","#ca0020")) +
 scale_fill_manual(name = "Evolution history",
                    labels=c("C_C" = "Control",
                             "Ctrl_Ambiant" = "Ambient x NoPred" ,
                              "Ctrl_Warm" = "Warm x NoPred",
                             "Pred_Ambiant" = "Ambient x Pred" ,
                             "Pred_Warm" = "Warm x Pred" ),
                    values = c("black","#92c5de","#f4a582","#0571b0","#ca0020")) +
  guides(shape = guide_legend(override.aes = list(size = 5))) +
  xlab("Experimental temperature") +
  ylab("Logit Decompo Rate") +
  scale_x_continuous(breaks = data_decompo_clean$TempExpNum) +
  theme_LO_sobre 
plot_predict_decompo


# cowplot::save_plot("Plot_predict_logitrate_control.pdf",
#                    plot_predict_decompo, base_height = 10/cm(1),
#                    base_width = 15/cm(1), dpi = 610)

```




# 2. ANALYSIS CORRELATION
## Correlation 
```{r }
# Packages
# ---- 1. Filtrer les températures communes ----
datamerged_filt <- datamerged %>%
  filter(TempExpNum %in% c(5, 15, 27))

data_decompo_filt <- data_decompo_clean %>%
  filter(TempExpNum %in% c(5, 15, 27))

# ---- 2. Moyennes par Population × Temp ----
traits_mean <- datamerged_filt %>%
  group_by(Pop, TempExpNum) %>%
  summarise(Slope_Corrected = mean(Slope_Corrected, na.rm = TRUE),
            .groups = "drop")
  # summarise(Mass_Ind = mean(Mass_Ind, na.rm = TRUE),
  #           Slope_Corrected = mean(Slope_Corrected, na.rm = TRUE),
  #           .groups = "drop")


mass_mean <- datamerged %>%
  group_by(Pop) %>%
  summarise(Mass_Ind = mean(Mass_Ind, na.rm = TRUE),
            .groups = "drop")

decomp_mean <- data_decompo_filt %>%
  group_by(Pop, TempExpNum) %>%
  summarise(Deg_Rate_Raffard = mean(Deg_Rate_Raffard, na.rm = TRUE),
            .groups = "drop")

# ---- 3. Fusionner les datasets ----
df_pop <- left_join(decomp_mean, traits_mean,
                    by = c("Pop", "TempExpNum"))
dfmean_pop <- left_join(decomp_mean, mass_mean, ############A FINIR ICI
                    by = c("Pop"))


# Vérification
head(df_pop)
head(df_pop)

# --
# ---- 4. Corrélations ----
# Décomposition ~ slope
cor_slope <- cor.test(df_pop$Deg_Rate_Raffard,
                      df_pop$Slope_Corrected,
                      use = "complete.obs")

# Décomposition ~ masse
cor_mass <- cor.test(dfmean_pop$Deg_Rate_Raffard,
                     dfmean_pop$Mass_Ind,
                     use = "complete.obs")

cor_slope
cor_mass

# ---- 5. Modèle de régression linéaire ----
# mod <- lm(Deg_Rate_Raffard ~ Slope_Corrected + Mass_Ind, data = df_pop)
# anova(mod)
# 0.00003781/(0.00003781+0.00020013+0.00162003)
# 0.00020013/(0.00003781+0.00020013+0.00162003)

# R² global
# rsq_total <- rsq::rsq(mod, adj = TRUE)
# 
# 
# # R² partiels (semi-partial R² pour chaque prédicteur)
# rsq_part <- rsq::rsq.partial(mod)
# 
# rsq_total
# rsq_part

## PRObleme petit echantillon 
#donc en vrai: 7.9% de la variance expliqué
#$partial.rsq [1] 0.1127361 0.1099502 -> Permet juste de dire l'un par rapport à l'autre
#donc dans notre cas, les deux exlique la meme quantité de variance 



# ---- 6. Visualisations ----
# Relation avec le slope
ggplot(df_pop, aes(x = -Slope_Corrected, y = Deg_Rate_Raffard)) +
  geom_point(aes(color = factor(TempExpNum))) +
  geom_smooth(method = "lm", se = FALSE, col ="black") +
  labs(x = "Metabolic rate (Slope_Corrected)",
       y = "Decomposition (Deg_Rate_Raffard)",
       color = "Temp")

# Relation avec la masse
ggplot(dfmean_pop, aes(x = Mass_Ind, y = Deg_Rate_Raffard)) +
  geom_point(aes(color = factor(TempExpNum))) +
  geom_smooth(method = "lm", se = FALSE, col="black") +
  labs(x = "Body size (Mass_Ind)",
       y = "Decomposition (Deg_Rate_Raffard)",
       color = "Temp")
``` 



## Plot with SD
```{r }


# Pour le dataset des traits
traits_summary <- datamerged_respiro_clean %>%
  filter(TempExpNum %in% c(5,15,27)) %>%
  group_by(Pop, TempExpNum) %>%
  summarise(
    Slope_mean = mean(Slope_Pos, na.rm=TRUE),
    Slope_sd = sd(Slope_Pos, na.rm=TRUE),
    Slope_se = Slope_sd / sqrt(n()),
    n_traits = n(),
    .groups = "drop"
  )



# Pour le dataset des mass
mass_summary <- datamerged %>%
  group_by(Pop) %>%
  summarise(
    Mass_mean = mean(Mass_Ind, na.rm=TRUE),
    Mass_sd = sd(Mass_Ind, na.rm=TRUE),
    Mass_se = Mass_sd / sqrt(n()),
    n_traits = n(),
    .groups = "drop"
  )


# Pour le dataset de décomposition
decomp_summary <- data_decompo_clean %>%
  filter(TempExpNum %in% c(5,15,27)) %>%
  group_by(Pop, TempExpNum) %>%
  summarise(
    Deg_mean = mean(Deg_Rate_Raffard, na.rm=TRUE),
    Deg_sd = sd(Deg_Rate_Raffard, na.rm=TRUE),
    Deg_se = Deg_sd / sqrt(n()),
    n_decomp = n(),
    .groups = "drop"
  )

# Fusionner
df_pop <- left_join(decomp_summary, traits_summary,
                    by=c("Pop", "TempExpNum"))
df_pop_mass <- left_join(decomp_summary, mass_summary,
                    by=c("Pop"))
# library(boot)
# 
# # Fonction de corrélation bootstrap
# corr_boot <- function(data, indices) {
#   d <- data[indices, ]
#   cor(d$Deg_mean, d$Slope_mean)
# }
# 
# set.seed(123)
# 
# 
# results <- boot(df_pop, statistic=corr_boot, R=1000)
# boot.ci(results, type="perc")
# 
# # Corrélation originale (rho)
# rho_orig <- results$t0
# rho_orig

#La corrélation bootstrap entre Deg_mean et Slope_mean est très faible et l’intervalle de confiance inclut 0 :
# 
# 𝜌 ∈ [ − 0.42 , 0.13 ]
# ρ∈[−0.42,0.13]
# Interprétation
# 
# Pas de corrélation significative détectée
# 
# L’intervalle inclut 0 → aucune preuve solide que la décomposition varie systématiquement avec le taux métabolique à l’échelle Population × Temp.
# 
# Amplitude de l’incertitude
# L’intervalle est large, ce qui reflète :
# le nombre limité de populations (n ≈ 30)
# la variation intra-population.
# Pourquoi utiliser le bootstrap
# Il intègre la variance des deux jeux de données différents.

#C’est plus fiable que cor() simple, car tu ne regardes pas seulement la moyenne mais aussi la variation autour de cette moyenne.

# Plot Décomposition vs Slope
Plot_decompo_Slope <- ggplot(df_pop, aes(x=Slope_mean, y=Deg_mean, color=factor(TempExpNum))) +
  geom_point(size=3) +
  geom_errorbar(aes(ymin=Deg_mean-Deg_se, ymax=Deg_mean+Deg_se), width=0.0001) +
  geom_errorbarh(aes(xmin=Slope_mean-Slope_se, xmax=Slope_mean+Slope_se), height=0.0001) +
  #geom_smooth(method="lm", col = "black") +
  labs(x="Metabolic rate (Slope_uncorrected)", y="Decomposition (Deg_Rate_Raffard)",
       color="Temp (°C)") +
  theme_classic()
Plot_decompo_Slope


# Plot Décomposition vs Mass
plotdecompomass <- ggplot(df_pop_mass, aes(x=Mass_mean, y=Deg_mean)) +
  geom_point( aes(color=factor(TempExpNum)) , size=3) +
  geom_errorbar(aes(ymin=Deg_mean-Deg_se, ymax=Deg_mean+Deg_se, color=factor(TempExpNum)), width=0.0001) +
  geom_errorbarh(aes(xmin=Mass_mean-Mass_se, xmax=Mass_mean+Mass_se, color=factor(TempExpNum)), height=0.00001) +
  #geom_smooth(method="lm", col = "black") +
  labs(x="Body size (Mass_Ind)", y="Decomposition (Deg_Rate_Raffard)",
       color="Temp (°C)") +
  theme_classic()
plotdecompomass

# cowplot::save_plot("Plot_Decompo_vs_Respiro.pdf",
#                    Plot_decompo_Slope, base_height = 10/cm(1),
#                    base_width = 12/cm(1), dpi = 610)
# cowplot::save_plot("Plot_Decompo_vs_Mass.pdf",
#                    plotdecompomass, base_height = 10/cm(1),
#                    base_width = 12/cm(1), dpi = 610)

```






# 3. PST FST
## 3.1- Estimate mean et slope 
### Body mass
```{r }
SUM_Mass <- datamerged %>%
  group_by(Pop, EvolHistory) %>%
  summarise(Mean = mean(Mass_Ind, na.rm = TRUE), .groups = "drop") 


ggplot(SUM_Mass, aes(x = Mean, y = EvolHistory, color = EvolHistory)) +
  geom_point(position = position_jitter(width = 0, height = 0)) +
  theme_minimal()

```


### Respiro
```{r }
# SUM_Respi <- datamerged_respiro_clean %>%
#   group_by(Pop, EvolHistory) %>%
#   summarise(Mean = mean(log(Slope_Pos), na.rm = TRUE), .groups = "drop") 
# 
# 
# # Modele 
# mod <- lm(log(Slope_Pos) ~ TempExpNum*Pop + I(TempExpNum^2)*Pop,
#           data = datamerged_respiro_clean)



### Non-linear model WITHOUT random effects, using LRT
# mod <- lm(Slope_Corrected ~ TempExpNum*Pop + TempExpNumSquare*Pop, data = datamerged)
# newdat <- expand_grid(TempExpNum = seq(min(datamerged$TempExpNum),
#                                       max(datamerged$TempExpNum),
#                                       length.out = 100), 
#                      Pop = unique(levels(datamerged$Pop)))
# newdat$TempExpNumSquare <- newdat$TempExpNum*newdat$TempExpNum
# newdat$Linear <- predict(mod, newdata = newdat, re.form = NA)
# 
# plot_rawdata + geom_line(data = newdat, 
#                          aes(x = TempExpNum, y = Linear, group = Pop))

#Probleme ici c'est quadratique donc on prend la pente instantannée
# Extraire la pente (dérivée par rapport à Temp) pour chaque Pop, à une valeur de Temp donnée
#IL FAUT CHOISIR LA VALEUR! 
# slopes <- emmeans::emtrends(mod, ~ Pop | TempExpNum, var = "TempExpNum",
#                             at = list(TempExpNum = c(10))) %>%
#   as.data.frame() %>%
#   select(Pop, Slope = TempExpNum.trend)
# slopes


# Merge avec SUM_Respi
# SUM_Respi <- SUM_Respi %>%
#   left_join(slopes, by = "Pop")



#Predictiosn with NLMER
### BEST MODEL
# nlme_best <- lme(log(Slope_Pos)  ~  ns(TempExpNum, 3) + log(Mass_Ind),
#     random = ~1 | Pop,
#     weights = varPower(form = ~ TempExpNum),  
#   data = datamerged_respiro_clean,
#   method = "REML")


nlme_pop <- nlme::gls(log(Slope_Pos) ~ ns(TempExpNum, 3)*Pop + log(Mass_Ind),
  weights = varPower(form = ~ TempExpNum),
  data = datamerged_respiro_clean,
  method = "REML")


dat_predict_respiro_pop <- expand.grid(TempExpNum = seq(min(datamerged_respiro_clean$TempExpNum),
                                      max(datamerged_respiro_clean$TempExpNum),
                                      length.out = 1000), 
                                  Mass_Ind = mean(datamerged_respiro_clean$Mass_Ind), 
                                  Pop = unique(datamerged_respiro_clean$Pop))


# Estimate 
dat_predict_respiro_pop$predict <- predict(nlme_pop, 
                                           newdata = dat_predict_respiro_pop)

# 2. Extract one EvolHistory per Pop
pop_history <- unique(datamerged_respiro_clean[, c("Pop", "EvolHistory")])
dat_predict_respiro_pop <- merge(dat_predict_respiro_pop, pop_history, by = "Pop", all.x = TRUE)



####################################
############################ PLOT 
####################################


plot_predict_respiro <- ggplot(data = dat_predict_respiro_pop,
        aes(x = TempExpNum, y = predict)) + 
  #facet_wrap(~EvolHistory) + 
  geom_jitter(data = datamerged_respiro_clean, 
                       aes(x = TempExpNum, y = log(Slope_Pos), 
                           color = interaction(Predpop,Tpop), 
                           shape = interaction(Predpop,Tpop)), 
                       alpha = 0.8, size = 0.8) + 
  geom_line(data = dat_predict_respiro_pop,
            aes(x = TempExpNum, 
                y = predict, 
                group = Pop),
            size = 0.5) + 
  scale_shape_manual(name = "Evolution history",
                    labels=c("Ctrl.Ambiant" = "Ambient x NoPred" ,
                             "Pred.Ambiant" = "Ambient x Pred" ,
                              "Ctrl.Warm" = "Warm x NoPred",
                             "Pred.Warm" = "Warm x Pred" ),
                    values = c(16,17,16,17)) +  
  scale_color_manual(name = "Evolution history",
                    labels=c("Ctrl.Ambiant" = "Ambient x NoPred" ,
                             "Pred.Ambiant" = "Ambient x Pred" ,
                              "Ctrl.Warm" = "Warm x NoPred",
                             "Pred.Warm" = "Warm x Pred" ),
                    values = c("#92c5de","#0571b0","#f4a582","#ca0020")) +
 scale_fill_manual(name = "Evolution history",
                    labels=c("Ctrl.Ambiant" = "Ambient x NoPred" ,
                             "Pred.Ambiant" = "Ambient x Pred" ,
                              "Ctrl.Warm" = "Warm x NoPred",
                             "Pred.Warm" = "Warm x Pred" ),
                    values = c("#92c5de","#0571b0","#f4a582","#ca0020")) +
  guides(shape = guide_legend(override.aes = list(size = 5))) +
  xlab("Experimental temperature") +
  ylab("Log(Slope Pos)") +
  scale_x_continuous(breaks = datamerged$TempExpNum) +
  theme_LO_sobre 
plot_predict_respiro


# 
# cowplot::save_plot("Plot_Respiro_PerPop_PST_Allpoos.pdf",
#                    plot_predict_respiro, base_height = 10/cm(1),
#                    base_width = 15/cm(1), dpi = 610)



# # Extract valus 
# unique_pops <- unique(dat_predict_respiro_pop$Pop)
# result <- data.frame(Pop=character(),
#                      TempNum_min_predict=numeric(),
#                      TempNum_max_predict=numeric(),
#                      stringsAsFactors=FALSE)
# 
# for (p in unique_pops) {
#   subset_pop <- dat_predict_respiro_pop[dat_predict_respiro_pop$Pop == p, ]
#   min_temp <- subset_pop$TempExpNum[which.min(subset_pop$predict)]
#   max_temp <- subset_pop$TempExpNum[which.max(subset_pop$predict)]
#   
#   result <- rbind(result, data.frame(Pop=p, 
#                                      TempNum_min_predict=min_temp, 
#                                      TempNum_max_predict=max_temp))
# }
# 
# result



# BACK TRANSFORMATION
# Transformation inverse pour revenir sur l’échelle de Slope_Pos
# newdat$Slope_Pos_pred <- exp(newdat$pred)



# On s'assure que la prédiction est sur l'échelle du métabolisme (exp)
dat_predict_respiro_pop$pred_exp <- exp(dat_predict_respiro_pop$predict)

# Liste des populations
pops <- unique(dat_predict_respiro_pop$Pop)

# Préparer un tableau de résultats
SUM_Respi <- data.frame(Pop = pops,
                      min_temp = NA,
                      max_temp = NA,
                      mean_level = NA,
                      sd_shape = NA,
                      slope_low = NA,
                      slope_high = NA,
                      optimum_temp = NA)


temp_dataevolhistory <- aggregate(EvolHistory ~ Pop, data = datamerged_respiro_clean, FUN = unique)
SUM_Respi <- merge(SUM_Respi, 
                   temp_dataevolhistory[, c("Pop", "EvolHistory")], 
                   by = "Pop", all.x = TRUE, all.y = FALSE)
rm(temp_dataevolhistory)

# Boucle sur chaque population
for (i in seq_along(pops)) {
  
  sub <- dat_predict_respiro_pop[dat_predict_respiro_pop$Pop == pops[i], ]
  
  
  SUM_Respi$min_temp[i] <- sub$TempExpNum[which.min(sub$pred_exp)]
  SUM_Respi$max_temp[i]   <- sub$TempExpNum[which.max(sub$pred_exp)]
  
  
  # Niveau moyen et "pointuosité"
  SUM_Respi$mean_level[i] <- mean(sub$pred_exp, na.rm = TRUE)
  SUM_Respi$sd_shape[i]   <- sd(sub$pred_exp, na.rm = TRUE)
  
  # Sensibilité basse température (ici entre points 1 et 20)
  SUM_Respi$slope_low[i] <- (sub$pred_exp[20] - sub$pred_exp[1]) / 
                          (sub$TempExpNum[20] - sub$TempExpNum[1])
  
  # Sensibilité haute température (ici entre les 180e et 200e points si ~200 valeurs)
  n <- nrow(sub)
  SUM_Respi$slope_high[i] <- (sub$pred_exp[n] - sub$pred_exp[n-20]) / 
                           (sub$TempExpNum[n] - sub$TempExpNum[n-20])
  
  # Optimum thermique
  SUM_Respi$optimum_temp[i] <- sub$TempExpNum[which.max(sub$pred_exp)]
}

SUM_Respi


# mean_level : moyenne de exp(predict) → niveau moyen du métabolisme
  # populations avec un métabolisme globalement élevé vs bas.
# sd_shape : écart-type de exp(predict) → mesure de la "pointuosité" vs "platitude"
  # faible → courbe presque plate → population tolérante à la T°,
  # forte → courbe bien définie (optimum marqué).
# slope_low : pente entre ~5ème et ~10ème quantile de température
# slope_high : pente entre ~90ème et ~95ème quantile
  # indiquent la force de la réponse aux extrêmes.
# optimum_temp : température où la respiration est maximale (si bien défini).
  # donc correspoind à max_temp


# Regarder correlation entre ces variables

# 1. Garder uniquement les colonnes numériques
num_vars <- SUM_Respi[, c("min_temp", "max_temp", "mean_level", 
                        "sd_shape", "slope_low", "slope_high", "optimum_temp")]
# 2. Matrice de corrélation
cor_mat <- cor(num_vars, use = "complete.obs")
# 3. Conversion en format long pour ggplot
cor_df <- as.data.frame(as.table(cor_mat))
colnames(cor_df) <- c("Var1", "Var2", "Correlation")
cor_df <- cor_df[as.numeric(cor_df$Var1) < as.numeric(cor_df$Var2), ]
# 4. Heatmap
ggplot(cor_df, aes(x = Var1, y = Var2, fill = Correlation)) +
  geom_tile(color = "white") +
  geom_text(aes(label = round(Correlation, 2)), size = 3) +
  scale_fill_gradient2(low = "blue", high = "red", mid = "white",
                       midpoint = 0, limit = c(-1, 1)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title = element_blank()) +
  labs(title = "Heatmap des corrélations entre métriques de populations",
       fill = "Corrélation")



##### Metrics
ggplot(SUM_Respi, aes(x = mean_level, y = EvolHistory, color = EvolHistory)) +
  geom_point(position = position_jitter(width = 0, height = 0)) +
  ggtitle("Respiro") + 
  theme_minimal()

ggplot(SUM_Respi, aes(x = sd_shape, y = EvolHistory, color = EvolHistory)) +
  geom_point(position = position_jitter(width = 0, height = 0)) +
  ggtitle("Respiro") + 
  theme_minimal()

ggplot(SUM_Respi, aes(x = optimum_temp, y = EvolHistory, color = EvolHistory)) +
  geom_point(position = position_jitter(width = 0, height = 0)) +
  theme_minimal() + 
  ggtitle("Respiro")

```





### Decompo
```{r }
SUM_Decompo <- data_decompo_clean %>%
  group_by(Pop, EvolHistory) %>%
  summarise(Mean = mean(Deg_Rate_Raffard, na.rm = TRUE), .groups = "drop") 

# Model
mod <- lm(Deg_Rate_Raffard ~ TempExpNum*Pop, data = data_decompo_clean)

coefs <- coef(mod)
pops <- levels(data_decompo_clean$Pop)
pops <- pops[pops != "C"]

# Initialiser les pentes avec NA
slopes <- data.frame(Pop = pops, Slope = NA_real_)
slopes$Slope[1] <- coefs["TempExpNum"]

# Les autres Pop (on aligne correctement les interactions)
for (i in 2:length(pops)) {
  term <- paste0("TempExpNum:Pop", pops[i])
  slopes$Slope[i] <- coefs["TempExpNum"] + coefs[term]
}


# Merge
SUM_Decompo <- data_decompo_clean %>%
  group_by(Pop, EvolHistory) %>%
  summarise(Mean = mean(Deg_Rate_Raffard, na.rm = TRUE), .groups = "drop") %>%
  left_join(slopes, by = "Pop")

```





## 3.2- Estimate GLMM

### Function to extract PST
```{r }

mod_slope_decompo = glmmTMB(Slope~1+(1|EvolHistory/Pop), data = SUM_Decompo)
model=mod_slope_decompo

compute_PST_glmmTMB <- function(model, group_name = "EvolHistory") {
  # Extract conditional random effect SDs
  
  # Get VarCorr object
  vc <- VarCorr(model)

  # Conditional random effects
  cond_var <- c(Pop.EvolHistory = vc$cond$`Pop:EvolHistory`[1,1],
    EvolHistory = vc$cond$EvolHistory[1,1])


  # Assign names automatically from VarCorr
  rand_names <- names(cond_var)
  
  
  if(length(rand_names) != length(cond_var)) rand_names <- paste0("RE", seq_along(rand_var))
  names(cond_var) <- rand_names
  
  # Residual variance
  var_resid <- sigma(model)^2
  
  
  # Total variance
  total_var <- sum(cond_var) + var_resid
  
  # Variance of focal group
  if(!group_name %in% names(cond_var)) stop(paste("Group", group_name, "not found"))
  var_group <- cond_var[group_name]
  
  # PST
  PST <- var_group / total_var
  
  # Build table
  variance_table <- data.frame(
    Group = c(names(cond_var), "Residual", "Total"),
    Variance = c(cond_var, var_resid, total_var))
  
  return(list(PST = PST, table = variance_table))
}

# Usage
res <- compute_PST_glmmTMB(mod_slope_decompo)
res$PST       # PST value
res$table     # Table of variance components


```

### Models GlmmTMB - Real data
```{r }
library(glmmTMB)

data_sum_PST <- data.frame("Var" = c("Mean_Mass",
                                     "Mean_Respiro", 
                                     "Slope_Optimum_Respiro",
                                     'Slope_Sd_Respiro', 
                                     "Mean_Decompo", 
                                     "Slope_Decompo"), 
                           "PST" = NA, 
                           "CI.low" = NA, 
                           "CI.up" = NA)


# MASS
mod_mean_mass=glmmTMB(Mean~1+(1|EvolHistory/Pop), data = SUM_Mass)
summary(mod_mean_mass)
res <- compute_PST_glmmTMB(mod_mean_mass)
res$PST
data_sum_PST[data_sum_PST$Var=="Mean_Mass",]$PST <- res$PST

#glm.boot()



#Donc valeur de PST
#EvolHistory : 6.359e11 -> Soit en pourcentage: 6.359e-11/(2.896e-03+6.359e-11+7.936e-05) 
#Pop/EvolHistory :2.896e-03 -> Soit en pourcentage: 2.896e-03/(2.896e-03+6.359e-11+7.936e-05) 
# Pour le plot prendre : pourcentage de EvolHistory donc 6.359e-11/(2.896e-03+6.359e-11+7.936e-05) 


# RESPIRO 
mod_mean_respiro=glmmTMB(mean_level~1+(1|EvolHistory/Pop), data = SUM_Respi)
summary(mod_mean_respiro)
res <- compute_PST_glmmTMB(mod_mean_respiro)
res$PST
data_sum_PST[data_sum_PST$Var=="Mean_Respiro",]$PST <- res$PST

mod_slope_respiro=glmmTMB(optimum_temp~1+(1|EvolHistory/Pop), data = SUM_Respi)
summary(mod_slope_respiro)
res <- compute_PST_glmmTMB(mod_slope_respiro)
res$PST
data_sum_PST[data_sum_PST$Var=="Slope_Optimum_Respiro",]$PST <- res$PST


mod_slope_respiro=glmmTMB(sd_shape~1+(1|EvolHistory/Pop), data = SUM_Respi)
summary(mod_slope_respiro)
res <- compute_PST_glmmTMB(mod_slope_respiro)
res$PST
data_sum_PST[data_sum_PST$Var=="Slope_Sd_Respiro",]$PST <- res$PST


# DECOMPO 
mod_mean_decompo = glmmTMB(Mean~1+(1|EvolHistory/Pop), data = SUM_Decompo)
summary(mod_mean_decompo)
res <- compute_PST_glmmTMB(mod_mean_decompo)
res$PST
data_sum_PST[data_sum_PST$Var=="Mean_Decompo",]$PST <- res$PST

mod_slope_decompo = glmmTMB(Slope~1+(1|EvolHistory/Pop), data = SUM_Decompo)
summary(mod_slope_decompo)
res <- compute_PST_glmmTMB(mod_slope_decompo)
res$PST
data_sum_PST[data_sum_PST$Var=="Slope_Decompo",]$PST <- res$PST

```





### Permutation - Confidence interval
```{r }


nsimul <- 1000
res_simul <- numeric(nsimul) 

# Mean_Mass
res_simul <- numeric(nsimul) 
for (i in 1:nsimul) {
  idx_remove <- sample(1:nrow(SUM_Mass), size = 1)
  SUM_Mass_subset <- SUM_Mass[-idx_remove, ]
  mod_mean_mass <- glmmTMB(Mean ~ 1 + (1 | EvolHistory/Pop), data = SUM_Mass_subset)
  res <- compute_PST_glmmTMB(mod_mean_mass)
  res_simul[i] <- res$PST
}

data_sum_PST[data_sum_PST$Var=="Mean_Mass",]$CI.low <- quantile(res_simul,0.025)
data_sum_PST[data_sum_PST$Var=="Mean_Mass",]$CI.up <- quantile(res_simul,0.975)



# RESPIRO 
res_simul <- numeric(nsimul) 
for (i in 1:nsimul) {
  idx_remove <- sample(1:nrow(SUM_Respi), size = 1)
  SUM_subset <- SUM_Respi[-idx_remove, ]
  mod_subset <- glmmTMB(mean_level ~ 1 + (1 | EvolHistory/Pop), data = SUM_subset)
  res <- compute_PST_glmmTMB(mod_subset)
  res_simul[i] <- res$PST
  rm(mod_subset,SUM_subset,res)
}

data_sum_PST[data_sum_PST$Var=="Mean_Respiro",]$CI.low <- quantile(res_simul,0.025)
data_sum_PST[data_sum_PST$Var=="Mean_Respiro",]$CI.up <- quantile(res_simul,0.975)


#SLOPE RESIRO
res_simul <- numeric(nsimul) 
for (i in 1:nsimul) {
  idx_remove <- sample(1:nrow(SUM_Respi), size = 1)
  SUM_subset <- SUM_Respi[-idx_remove, ]
  mod_subset <- glmmTMB(optimum_temp ~ 1 + (1 | EvolHistory/Pop), data = SUM_subset)
  res <- compute_PST_glmmTMB(mod_subset)
  res_simul[i] <- res$PST
  rm(mod_subset,SUM_subset,res)
}

data_sum_PST[data_sum_PST$Var=="Slope_Optimum_Respiro",]$CI.low <- quantile(res_simul,0.025)
data_sum_PST[data_sum_PST$Var=="Slope_Optimum_Respiro",]$CI.up <- quantile(res_simul,0.975)

#Slope SD 
res_simul <- numeric(nsimul) 
for (i in 1:nsimul) {
  idx_remove <- sample(1:nrow(SUM_Respi), size = 1)
  SUM_subset <- SUM_Respi[-idx_remove, ]
  mod_subset <- glmmTMB(sd_shape ~ 1 + (1 | EvolHistory/Pop), data = SUM_subset)
  res <- compute_PST_glmmTMB(mod_subset)
  res_simul[i] <- res$PST
  rm(mod_subset,SUM_subset,res)
}

data_sum_PST[data_sum_PST$Var=="Slope_Sd_Respiro",]$CI.low <- quantile(res_simul,0.025)
data_sum_PST[data_sum_PST$Var=="Slope_Sd_Respiro",]$CI.up <- quantile(res_simul,0.975)



# DECOMPO 
res_simul <- numeric(nsimul) 
for (i in 1:nsimul) {
  idx_remove <- sample(1:nrow(SUM_Decompo), size = 1)
  SUM_subset <- SUM_Decompo[-idx_remove, ]
  mod_subset <- glmmTMB(Mean ~ 1 + (1 | EvolHistory/Pop), data = SUM_subset)
  res <- compute_PST_glmmTMB(mod_subset)
  res_simul[i] <- res$PST
  rm(mod_subset,SUM_subset,res)
}

data_sum_PST[data_sum_PST$Var=="Mean_Decompo",]$CI.low <- quantile(res_simul,0.025)
data_sum_PST[data_sum_PST$Var=="Mean_Decompo",]$CI.up <- quantile(res_simul,0.975)


res_simul <- numeric(nsimul) 
for (i in 1:nsimul) {
  idx_remove <- sample(1:nrow(SUM_Decompo), size = 1)
  SUM_subset <- SUM_Decompo[-idx_remove, ]
  mod_subset <- glmmTMB(Slope ~ 1 + (1 | EvolHistory/Pop), data = SUM_subset)
  res <- compute_PST_glmmTMB(mod_subset)
  res_simul[i] <- res$PST
  rm(mod_subset,SUM_subset,res)
}

data_sum_PST[data_sum_PST$Var=="Slope_Decompo",]$CI.low <- quantile(res_simul,0.025)
data_sum_PST[data_sum_PST$Var=="Slope_Decompo",]$CI.up <- quantile(res_simul,0.975)



```




###  Plot
```{r }
library(ggtext)  # enables HTML/Markdown in titles

data_sum_PST$PST_percent = data_sum_PST$PST*100
data_sum_PST$CI.low_percent = data_sum_PST$CI.low*100
data_sum_PST$CI.up_percent = data_sum_PST$CI.up*100

data_sum_PST$Var <- factor(data_sum_PST$Var, levels = rev(unique(data_sum_PST$Var)))

plotPSTFST <- ggplot(data_sum_PST, aes(x = PST_percent, y = Var)) +
  #geom_hline(yintercept = 1:length(unique(data_sum_PST$Var)), color = "gray95", size = 0.2) +
  geom_point(size = 3) +
  geom_errorbarh(aes(xmin = CI.low_percent, xmax = CI.up_percent), height = 0.2, color = "black") +
  geom_vline(xintercept = 21.67, lty = 1, color = "indianred2") + 
  geom_vline(xintercept = 20.98, lty = 2, color = "indianred2") + 
  geom_vline(xintercept = 22.34, lty = 2, color = "indianred2") + 
  scale_x_continuous(limits = c(0, 100), labels = scales::percent_format(scale = 1)) +
  labs(
    x = "<span style='color:indianred2;'>Fst  </span> <span style='color:white;'>------- </span> <span style='color:black;'>Pst        </span> <span style='color:white;'>------_____-- </span>", 
    y=NULL) +
  scale_y_discrete(breaks = unique(data_sum_PST$Var), 
                   labels = c("Mean Mass", "Mean metabolic rate",
                              "Temperature-dependent\noptimum metabolic rate",
                              "Temperature-dependent\nvariation metabolic rate",
                              "Mean decomposition rate", "Temperature-dependent\ndecomposition rate")) +
  theme_LO_sobre +
  theme(axis.title.x = element_markdown())  # <- override after your theme
plotPSTFST

plotPSTFST <- ggplot(data_sum_PST, aes(x = PST_percent, y = Var)) +
  geom_point(aes(color = Var), size = 3) +
  geom_errorbarh(aes(xmin = CI.low_percent, xmax = CI.up_percent, color = Var), 
                 height = 0.2) +
  geom_vline(xintercept = 21.67, lty = 1, color = "indianred2") + 
  geom_vline(xintercept = 20.98, lty = 2, color = "indianred2") + 
  geom_vline(xintercept = 22.34, lty = 2, color = "indianred2") + 
  scale_x_continuous(limits = c(0, 100), labels = scales::percent_format(scale = 1)) +
  labs(
    x = "<span style='color:indianred2;'>Fst  </span> <span style='color:white;'>------- </span> <span style='color:black;'>Pst        </span> <span style='color:white;'>------_____-- </span>", 
    y = NULL) +
  scale_y_discrete(breaks = unique(data_sum_PST$Var), 
    labels = c("Mean body mass", "Mean metabolic rate",
               "Temperature-dependent\noptimum metabolic rate",
               "Temperature-dependent\nvariation metabolic rate",
               "Mean decomposition rate", 
               "Temperature-dependent\ndecomposition rate")) +
  scale_color_manual(values = c("Mean_Mass" = "#2176AE",
      "Mean_Respiro" = "black",
      "Slope_Optimum_Respiro" = "#2176AE",
      "Slope_Sd_Respiro" = "black",
      "Mean_Decompo" = "#2176AE",
      "Slope_Decompo" = "#2176AE")) +
  theme_LO_sobre +
  theme(axis.title.x = element_markdown(),
        legend.position = "none")  # hide legend if not needed

plotPSTFST

# 
# cowplot::save_plot("Plot_Fig5_Pst_Fst_nsim1000.pdf",
#                    plotPSTFST, base_height = 12/cm(1),
#                    base_width = 17/cm(1), dpi = 610)
# 
# 

```


